---
title: "no_raising_to_fishing_fleet"
output: html_document
date: '2022-04-29'
---


This document give a quick analysis of different way raise IATTC data at the beginning of the process.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE
)
library(readtext)
library(flextable)
set_flextable_defaults(
  font.size = 30,
  font.color = "black",
  table.layout = "fixed",
  digits = NULL,
  theme_fun = "theme_box"
  )
options(scipen=999)
library(dplyr)
library(stringr)
library(readr)
library(webshot)
if(require("htmltools"))
div(flextable_html_dependency())
```

```{r}
mapping_codelist <- readRDS("data/mapping_codelist.rds")
raising_fishingfleet_to_schooltype <- readRDS("data/raising_fishing_fleet_to_schooltype.rds")
raising_schooltype_to_fishingfleet <- readRDS("data/raising_schooltype_to_fishingfleet.rds")
```

# Raising to fishing fleet

```{r}
comp <- gdata::combine(mapping_codelist, raising_fishingfleet_to_schooltype, raising_schooltype_to_fishingfleet)
comp$unit <- str_replace(comp$unit, "MTNO","MT")
comp$unit <- str_replace(comp$unit, "NOMT","NO")
comp <-  comp%>% group_by(source, time_start, unit) %>% summarise(Value = sum(value)) %>% mutate(time_start = as.Date(time_start)) 
```


```{r}
library(lubridate)
comp_year <- comp %>% mutate(Year =lubridate::year(time_start)) %>%ungroup() %>%  group_by(Year, unit, source) %>% summarise(Value = sum(Value))
```
```{r}
library(ggplot2)

ggplot(comp_year)+
  aes(x = Year, y = Value, colour = source) +
  geom_line(size = 0.5) +
  scale_color_hue(direction = 1) +
  theme_minimal() +
  facet_wrap(vars(unit), scales = "free_y")
```



The difference between the two dataset is `r sum((raising_fishingfleet_to_schooltype %>% filter(unit == "MT"))$value) - sum((raising_schooltype_to_fishingfleet %>% filter(unit == "MT"))$value)` in tons and `r sum((raising_fishingfleet_to_schooltype %>% filter(unit == "NO"))$value) - sum((raising_schooltype_to_fishingfleet %>% filter(unit == "NO"))$value)` in number of fish.

# Other raising_schooltype_to_fishingfleet 

We could also decide to keep the data from other rfmo's if there is no equivalent in year, area. 

The results would be the following : 

