---
title: "Analyse georeferenced"
author: "Bastien Grasset"
date: "09/02/2022"
output:
  html_document:
    toc: true
    theme: united
    number_sections: true
params: 
  init: "~/Documents/Tunaatlas_level1/jobs/level0_FAL/entities/global_catch_1deg_level0/Markdown/rawdata/rds.rds"
  filter_species: [FAL]
  filter_source_authority: "NULL"
  filter_gear: "NULL"
  filter_fishingfleet: "NULL"
  filter_time_start: "NULL"
  filter_time_end: "NULL"
  filter_cat_geo: "NULL"
  filter_catchtype: "NULL"
  filter_schooltype: "NULL"
  titre_dataset_1: "Nominal data after mapping"
  titre_dataset_2: "Mapcodelist"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r}
if(!(require(base))){ 
 install.packages(base) 
 (require(base))} 
 if(!(require(flextable))){ 
 install.packages(flextable) 
 (require(flextable))} 
 if(!(require(remotes))){ 
 install.packages(remotes) 
 (require(remotes))} 
 if(!(require(utils))){ 
 install.packages(utils) 
 (require(utils))} 
 if(!(require(stringr))){ 
 install.packages(stringr) 
 (require(stringr))} 
 if(!(require(knitr))){ 
 install.packages(knitr) 
 (require(knitr))} 
 if(!(require(DBI))){ 
 install.packages(DBI) 
 (require(DBI))} 
 if(!(require(odbc))){ 
 install.packages(odbc) 
 (require(odbc))} 
 if(!(require(sf))){ 
 install.packages(sf) 
 (require(sf))} 
 if(!(require(dplyr))){ 
 install.packages(dplyr) 
 (require(dplyr))} 
 if(!(require(kableExtra))){ 
 install.packages(kableExtra) 
 (require(kableExtra))} 
 if(!(require(readxl))){ 
 install.packages(readxl) 
 (require(readxl))} 
 if(!(require(readr))){ 
 install.packages(readr) 
 (require(readr))} 
 if(!(require(tidyr))){ 
 install.packages(tidyr) 
 (require(tidyr))} 
 if(!(require(ggplot2))){ 
 install.packages(ggplot2) 
 (require(ggplot2))} 
 if(!(require(stats))){ 
 install.packages(stats) 
 (require(stats))} 
 if(!(require(RColorBrewer))){ 
 install.packages(RColorBrewer) 
 (require(RColorBrewer))} 
 if(!(require(cowplot))){ 
 install.packages(cowplot) 
 (require(cowplot))} 
if(!require(sutdycatchesird)){
  if(!require(remotes)){
    install.packages("remotes")
  }
  require(remotes)
  install_github("BastienIRD/sutdycatchesird")
  require(sutdycatchesird)
}
 if(!(require(tmap))){ 
 install.packages(tmap) 
 (require(tmap))} 
 if(!(require(RPostgreSQL))){ 
 install.packages(RPostgreSQL) 
 (require(RPostgreSQL))} 
 

 

set_flextable_defaults(
  font.size = 10,
  font.color = "black",
  table.layout = "fixed",
  digits = 0,
  theme_fun = "theme_box"
  )

tmap_mode("view")
```


```{r}
drv <- dbDriver("PostgreSQL")      
con <- DBI::dbConnect(drv , dbname = "tunaatlas_sandbox", host = "db-tunaatlas.d4science.org", 
                 port = 5432,
                 user = "tunaatlas_u",
                 password = "21c0551e7ed2911")




kbl <- function(data) {
  knitr::kbl(data, booktabs = TRUE, digits = 2) %>% 
    kable_styling(latex_options =c("striped", "scale_down"))
}

```


```{r}
library(readxl)
species_group <-  read_excel("data/SPECIES_LIST_RFMO_WITH_ERRORS.xlsx") %>% janitor::clean_names() %>%  select(species_group, species_code) %>% rename(species = species_code)
colnames_to_keep <- c("fishingfleet",         "gear",                 "time_start",           "time_end",            
"geographic_identifier",           "species",                      
              "value",                "source_authority", "unit")

```


The purpose of this markdown is to describe the nominal dataset created on the global tunaatlas.

# The data

The analyzed data are :
- ***`r params$init` for the initial data***

The filters used are:

- on species: `r params$filter_species`
- on gears: `r params$filter_gear`
- on rfmos: `r params$filter_source_authority`
- on fleets: `r params$filter_fishing_fleet`
- on initial dates: `r params$filter_time_start`
- on final dates: `r params$filter_time_end`
- on geographical categories: `r params$filter_cat_geo`
- on catch types: `r params$filter_catchtype`


```{r}
# as.character(params$init)
# as.character(params$final)
last_path = function(x){tail(str_split(x,"/")[[1]],n=1)}
last_path_reduced = function(x){gsub("georef_dataset","",last_path(x))}

fonction_filtre = function(dataframe_tot_filter) {
  if (!(params$filter_species == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  species %in% params$filter_species)
  }
    if (!(params$filter_gear == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  gear %in% params$filter_gear)
    }    
  if (!(params$filter_source_authority == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  source_authority %in% params$filter_source_authority)
  }  
  if (!(params$filter_fishingfleet == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  fishingfleet %in% params$filter_fishingfleet)
  }
    if (!(params$filter_time_start == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  time_start %in% params$filter_time_start)
    }
      if (!(params$filter_time_end == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  time_end %in% params$filter_time_end)
      }
    if (!(params$filter_schooltype == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  schooltype %in% params$filter_schooltype)
  }
    if (!(params$filter_catchtype == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  catchtype %in% params$filter_catchtype)
    }
  
  if (!(params$filter_cat_geo == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  cat_geo %in% params$filter_cat_geo)
  }
    if (!(params$filter_catchtype == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  cat_geo %in% params$filter_catchtype)
    }

  # dataframe_tot_filter <- dataframe_tot_filter 
  # dataframe_tot_filter%>% mutate(unit = case_when(unit %in% c("MT","t","MTNO", "Tons")~ "Tons", unit %in% c("NO", "NOMT","no", "Number of fish")~"Number of fish"))
  cl_cwp_gear_level2 <- read_csv("data/cl_cwp_gear_level2.csv", 
    col_types = cols(Identifier = col_skip(), 
        Abbreviation = col_skip(), Name_Fr = col_skip(), 
        Name_Es = col_skip(), Name_Ar = col_skip()))

dataframe_tot_filter <- dataframe_tot_filter %>% full_join(cl_cwp_gear_level2, by = c("gear" = "Code"))
  
}

  
init <- fonction_filtre(readRDS(as.character(params$init)) %>% select(all_of(colnames_to_keep)) %>%  left_join(species_group, by = c("species"))%>% distinct() )


  if ((params$titre_dataset_1 == "NULL")){
    titre_1 <- last_path_reduced(as.character(params$init))
  } else {
    titre_1 <- params$titre_dataset_1
  }

```



```{r}
fonction_groupement = function(x, init){
  x  <-   enquo(x)
  groupement_1  <-   init %>% group_by(!!x ) %>% summarise(value_sum_1 = sum(value, na.rm=TRUE), number_lines1 = n())
}
```



```{r}
carte_init <- fonction_groupement(geographic_identifier,init)


Dimensions <- colnames(init)[colnames(init) != "unit" & colnames(init)!= "value"]
  # t <- init[0,] 
  t <- carte_init[0,]
  colnames(t )[1] <- "Precision"


for (i in Dimensions){
  temporaire <- fonction_groupement(.data[[i]],init)
  assign(paste0("test", i), temporaire)
  colnames(temporaire)[1] <- "Precision"

  print(i)
  t <- rbind(t, temporaire)
}
  
init_t <- init

      somme_init_t <- sum(init_t$value, na.rm = TRUE)



  
nb_ligne_init_millions <- nrow(init)/10^6

sum_valeur_init <- sum(init$value, na.rm = TRUE)/10^6


```



```{r}
library(rlang)




# ggplot(t)+geom_bar(mapping = aes(x = pourcentage, y = as.factor(class)))

Dimensions <- colnames(init)[colnames(init) != "unit" & colnames(init)!= "value"&
                               colnames(init)!= "time_start"&
                               colnames(init)!= "time_end"&
                               colnames(init)!= "geographic_identifier"]
  # t <- init[0,] 
```

## Catch evolutions

```{r}
captures_par_time <- testtime_start %>% mutate(Time = as.Date(time_start))%>% rename(`Captures table 1` = "value_sum_1")%>% pivot_longer(cols = c(`Captures table 1`), names_to = "Origin", values_to ="Captures")


ggplot(captures_par_time) +
  aes(
    x = Time,
    y = Captures,
    fill = Origin,
    colour = Origin,
    group = Origin
  ) +
  geom_line(size = 0.5) +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  theme_dark() +
  theme(legend.position = "top") +
  labs(x = "Time", y = "Captures")+
  facet_grid(scales = "free_y")
```

## Evolution of the cumulative catches

```{r}
captures_par_time <- captures_par_time %>% mutate(Time = as.Date(time_start))%>% arrange(time_start) %>% group_by(Origin) %>%  mutate(`Captures cumulées` = cumsum(`Captures`)) %>% distinct()

ggplot_capt_par_time = function(x){
  
  ggplot(captures_par_time) +
  aes(
    x = Time,
    y = `Captures cumulées`,
    colour = Origin
  ) +
  geom_line(size = 0.5) +
  scale_color_hue(direction = 1) +
  theme_minimal() +
  labs(x = "Time", y = "Cumulated captures")+guides(fill=guide_legend(title="Dataset"))
}

ggplot_capt_par_time("Tons")

```

```{r}
# library(cowplot)
fishing_fleet <- studycatchesird::pie_chart_2(fishingfleet, init)
source_authority <- studycatchesird::pie_chart_2(source_authority, init)
species <- studycatchesird::pie_chart_2(species, init)
species_group <- studycatchesird::pie_chart_2(species_group, init)
gear <- studycatchesird::pie_chart_2(gear, init)
Name_En <- studycatchesird::pie_chart_2(Name_En, init)

```

```{r}


species
# png(filename = "data/nominal_report/pie_chart_species.png")
# print(species)
# dev.off()
fishing_fleet
# png(filename = "data/nominal_report/pie_chart_fishing_fleet.png")
# print(fishing_fleet)
# dev.off()

source_authority
# png(filename = "data/nominal_report/pie_chart_source_authority.png")
# print(source_authority)
# dev.off()

species_group
# png(filename = "data/nominal_report/pie_chart_species_group.png")
# print(source_authority)
# dev.off()

Name_En
# png(filename = "data/nominal_report/pie_chart_source_authority.png")
# print(source_authority)
# dev.off()
# plot_grid(species, cat_geo, fishing_fleet,source_authority,species_group,  ncol = 1)
```

