---
title: "Comparison of two data sets at different levels/options of the tuna atlas"
author: "Bastien Grasset"
date: "09/02/2022"
output:
  html_document:
    toc: true
    theme: united
    number_sections: true
params: 
  init: "~/Documents/Tunaatlas_level1/jobs/20220501202640/entities/global_nominal_catch_firms_level0/Markdown/mapping/rds.rds"
  final: "~/Documents/Tunaatlas_level1/jobs/20220501202640/entities/global_nominal_catch_firms_level0/Markdown/SBF_filter/rds.rds"
  filter_species: "SBF"
  filter_source_authority: "NULL"
  filter_gear: "NULL"
  filter_fishingfleet: "NULL"
  filter_time_start: "NULL"
  filter_time_end: "NULL"
  filter_cat_geo: "NULL"
  filter_catchtype: "NULL"
  filter_schooltype: "NULL"
  titre_dataset_1: "Old_method"
  titre_dataset_2: "New_method"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r}
library(dplyr)
library(stringr)
library(readr)
library(ggplot2)
library(shiny)
library(tidyr)
library(DT)
library(kableExtra)
library(flextable)

set_flextable_defaults(
  font.size = 10,
  font.color = "black",
  table.layout = "fixed",
  digits = 0,
  theme_fun = "theme_box"
  )
options(scipen=999)
# tmap_mode("view")
```


```{r}
# drv <- dbDriver("PostgreSQL")      
# con <- DBI::dbConnect(drv , dbname = "tunaatlas", host = "db-tunaatlas.d4science.org", 
#                  port = 5432,
#                  user = "tunaatlas_u",
#                  password = "21c0551e7ed2911")



# dbExistsTable(con,"iattc_after_treatment")
# dbExistsTable(con,"/../area.area_wkt")

# summary(con)
# dbListTables(con)
# query <- "SELECT code, st_area(geom), geom from area.cwp_grid"
# world_sf <- st_read(con, query = query) 

# shapefile.fix <- st_make_valid(world_sf)%>% filter(!st_is_empty(.)) %>% mutate(cat_geo = as.factor(case_when(st_area == 1 ~ "1 deg", st_area == 25 ~ "5 deg", TRUE ~ "> 5 deg")))
# shape_without_geom  <- shapefile.fix %>% as_tibble() %>% select(-geom)
# options(scipen=999)

kbl <- function(data) {
  knitr::kbl(data, booktabs = TRUE, digits = 2) %>% 
    kable_styling(latex_options =c("striped", "scale_down"))
}

```


```{r}
library(readxl)
species_group <-  read_excel("data/SPECIES_LIST_RFMO_WITH_ERRORS.xlsx") %>% janitor::clean_names() %>%  select(species_group, species_code) %>% rename(species = species_code)
colnames_to_keep <- c("fishingfleet",         "gear",                 "time_start",           "time_end",            
"geographic_identifier","schooltype",           "species",              "catchtype",           
 "unit",                 "value",                "source_authority")

```


The purpose of this markdown is to describe the loss of data from the World Tuna Atlas following the different filters. 
It describes the differences between the initial data and the final data, and is intended for users of the final data who might be tempted to use it without taking into account the various filtering specificities.

# The data compared

The analyzed data are :
- ***`r params$init`*** for the initial data 
- ***`r params$final`*** for the final data.

The filters used are:

- on species: `r params$filter_species`
- on gears: `r params$filter_gear`
- on rfmos: `r params$filter_source_authority`
- on fleets: `r params$filter_fishing_fleet`
- on initial dates: `r params$filter_time_start`
- on final dates: `r params$filter_time_end`
- on geographical categories: `r params$filter_cat_geo`
- on catch types: `r params$filter_catchtype`


```{r}
# as.character(params$init)
# as.character(params$final)
last_path = function(x){tail(str_split(x,"/")[[1]],n=1)}
last_path_reduced = function(x){gsub("georef_dataset","",last_path(x))}

fonction_filtre = function(dataframe_tot_filter) {
  if (!(params$filter_species == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  species %in% params$filter_species)
  }
    if (!(params$filter_gear == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  gear %in% params$filter_gear)
    }    
  if (!(params$filter_source_authority == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  source_authority %in% params$filter_source_authority)
  }  
  if (!(params$filter_fishingfleet == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  fishingfleet %in% params$filter_fishingfleet)
  }
    if (!(params$filter_time_start == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  time_start %in% params$filter_time_start)
    }
      if (!(params$filter_time_end == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  time_end %in% params$filter_time_end)
      }
    if (!(params$filter_schooltype == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  schooltype %in% params$filter_schooltype)
  }
    if (!(params$filter_catchtype == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  catchtype %in% params$filter_catchtype)
    }
  
  if (!(params$filter_cat_geo == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  cat_geo %in% params$filter_cat_geo)
  }
    if (!(params$filter_catchtype == "NULL")){
    dataframe_tot_filter <-  dataframe_tot_filter %>% filter(
  cat_geo %in% params$filter_catchtype)
    }

  # dataframe_tot_filter <- dataframe_tot_filter 
  dataframe_tot_filter%>% mutate(unit = case_when(unit %in% c("MT","t","MTNO", "Tons")~ "Tons", unit %in% c("NO", "NOMT","no", "Number of fish")~"Number of fish"))
  
}


init <- fonction_filtre(readRDS(as.character(params$init)) %>% select(all_of(colnames_to_keep)))%>% left_join(species_group, by = c("species")) %>% distinct()


final <- fonction_filtre(readRDS(as.character(params$final))%>% select(all_of(colnames_to_keep)))%>% left_join(species_group, by = c("species"))%>% distinct()


  if ((params$titre_dataset_1 == "NULL")){
    titre_1 <- last_path_reduced(as.character(params$init))
  } else {
    titre_1 <- params$titre_dataset_1
  }


  if ((params$titre_dataset_2 == "NULL")){
    titre_2 <- last_path_reduced(as.character(params$final))
  } else {
    titre_2 <- params$titre_dataset_2
  }


# palette3_info <- brewer.pal.info[brewer.pal.info$category == "qual", ]  
# palette3_all <- unlist(mapply(brewer.pal, 
#                               palette3_info$maxcolors,
#                               rownames(palette3_info)))
# set.seed(2643598)  
# # palette3 <- sample(palette3_all, nrow(unique(df_i11_map$country)), replace=TRUE)
# palette3 <- sample(palette3_all, nrow(unique(init$species)), replace=TRUE)
# names(palette3) = init$species
# palette3

```



```{r}
fonction_groupement = function(x, init, final){
  x  <-   enquo(x)
  groupement_1  <-   init %>% group_by(!!x,unit) %>% summarise(value_sum_1 = sum(value, na.rm=TRUE), number_lines1 = n()) %>%mutate(value_sum1 = ifelse(is.na(value_sum_1), 0, value_sum_1))
  groupement_2  <-   final %>% group_by(!!x,unit) %>% summarise(value_sum_2 = sum(value, na.rm=TRUE), number_lines2 = n()) %>% mutate(value_sum_2 = ifelse(is.na(value_sum_2), 0, value_sum_2))
  
  fulljoin  <-   full_join(groupement_1, groupement_2) %>% 
    mutate(Perte_pourcent = 100*((value_sum_1 - value_sum_2)/value_sum_1))%>% mutate(Dimension = colnames(groupement_1[1])) %>%
    rename("Precision" = 1) %>% mutate(Precision = as.character(Precision)) %>% mutate(value_sum_2 = ifelse(is.na(value_sum_2), 0, value_sum_2))%>% mutate(Perte_pourcent = ifelse(is.na(Perte_pourcent), 100, Perte_pourcent)) %>% mutate(perte_nb_ligne = number_lines1 - number_lines2)%>% 
    mutate(Perte_en_milliers_de_tonne = (value_sum_1 - value_sum_2)/ 10^6) %>% 
           rename(`Loss (in %)` = Perte_pourcent,`Loss in millions of tons` = Perte_en_milliers_de_tonne, 
                  `Loss in number of lines` = perte_nb_ligne) %>% mutate_if(is.numeric, list(~replace_na(., 0))) %>% select(-c(value_sum1))
}
```



```{r}
carte_init <- fonction_groupement(species_group,init, final)


Dimensions <- colnames(init)[colnames(init) != "unit" & colnames(init)!= "value"]
  # t <- init[0,] 
  t <- carte_init[0,]


for (i in Dimensions){
  temporaire <- fonction_groupement(.data[[i]],init, final)
  assign(paste0("test", i), temporaire)
  
  t <- rbind(t, temporaire)
}
  
init_t <- init %>% filter(unit == "Tons")
init_no <- init %>% filter(unit == "Number of fish")
final_t <- final %>% filter(unit == "Tons")
final_no <- final %>% filter(unit == "Number of fish")
  
      somme_init_t <- sum(init_t$value, na.rm = TRUE)
    somme_init_no <- sum(init_no$value, na.rm = TRUE)
    somme_final_t <- sum(final_t$value, na.rm = TRUE)
    somme_final_no <- sum(final_no$value, na.rm = TRUE)
    

    perte_en_tonnes <- round(somme_init_t-somme_final_t)
    perte_en_tonnes_pourcent <- round(100*(somme_init_t-somme_final_t)/somme_init_t,2)
    perte_en_nombre <- round(somme_init_no-somme_final_no)
    perte_en_nombre_pourcent <-round(100*(somme_init_no-somme_final_no)/somme_init_no,2)
    # if(!is.null(perte_en_nombre_pourcent)){
    #   (if(perte_en_nombre_pourcent==-Inf) {perte_en_nombre_pourcent <- -100}
    #                               }

  
nb_ligne_init_millions <- nrow(init)/10^6
nb_ligne_final_millions<- nrow(final)/10^6

sum_valeur_init <- sum(init$value, na.rm = TRUE)/10^6
sum_valeur_final <- sum(final$value, na.rm = TRUE)/10^6

t$Dimension <-as.character(t$Dimension)
t$Precision <-as.character(t$Precision)

strates_perdues <- t %>% filter(`Loss (in %)` == 100)
nombre_strates_perdues <- nrow(strates_perdues)
nombres_de_strates_totales <- nrow(t)
pourcentage_strates_perdues <- 100-(100*((nombres_de_strates_totales-nombre_strates_perdues)/nombres_de_strates_totales))
rm(init_no, init_t, final_no, final_t)
gc()

strates_perdues_first_10 <- strates_perdues %>%ungroup %>%  group_by(Dimension)%>% slice(1:10) %>%select(Dimension, everything())
```

# Main differences

The number of lines goes from  `r nb_ligne_init_millions` millions in `r titre_1` to `r nb_ligne_final_millions` millions in `r titre_2`, which correspond to a difference of `r round(((nb_ligne_init_millions - nb_ligne_final_millions)/nb_ligne_init_millions)*100,5)`%.

The initial dataset has a total of `r somme_init_t` in tons and of `r round(somme_init_no)` in number of fish.
    
The final dataset has a total of  `r somme_final_t` in tons and of `r round(somme_final_no)` in number of fish.

The loss is `r perte_en_tonnes` in tons (**`r perte_en_tonnes_pourcent`%**). The loss is `r perte_en_nombre` in number of fish (**`r perte_en_nombre_pourcent`%**).

The stratas loss between the first one and the second one are : 

```{r}
qflextable(strates_perdues_first_10)
```


(only first 10 per Dimension showed), representing `r round(pourcentage_strates_perdues)` % of the total number of stratas.

# Loss

This section detail the different loss that observed between the dataframe `r titre_1` and `r titre_2`.

```{r}
disappearing_strates <- t %>% filter(value_sum_2 == 0)
```


```{r}
topn <- 5  
```

## The losses for each dimension

We will look for each dimension the `r topn` most important losses.

```{r paged.print=TRUE}
library(knitr)
library(DT)
library(kableExtra)
# kable(t %>%  filter(Dimension %in% c("species", "source_authority","cat_geo", "fishingfleet")) %>% mutate(Dimension = as.factor(Dimension)) %>%  group_by(unit, Dimension) %>% arrange(desc(`Loss (in %)`))   %>%   mutate(id = row_number())%>% ungroup() %>%  mutate(test = ifelse(id>(topn-1),"Others",as.character(Precision))) %>%mutate(Precision = test) %>%  mutate_if(is.character, as.factor)%>%select(-c(id, test)) %>% ungroup() %>%  group_by(Precision,unit, Dimension)%>% summarise_all(sum)  %>% group_by(unit, Dimension) %>%arrange(desc(`Loss (in %)`), desc(`Loss in millions of tons`)) %>%   group_split(unit))

valeur_totale <- sum(init$value, na.rm = TRUE)
ligne_totale <- nrow(init)

# unit_t <- t %>% filter(unit == "Tons")%>% filter(Dimension %in% c("species", "source_authority","cat_geo", "fishingfleet", "species_group")) %>% mutate(Dimension = as.factor(Dimension)) %>%  group_by( Dimension) %>% arrange(desc(`Loss (in %)`))   %>%   mutate(id = row_number())%>%   mutate(test = as.factor(ifelse(id>(topn-1),paste0("Others"),paste0(as.character(Precision))))) %>% ungroup() %>% group_by(Dimension,test) %>% summarise(across(is.numeric, sum)) %>% mutate(`Loss (in %)` = (`Loss in millions of tons`*1000000/value_sum_1)*100) %>% select(-id)%>%group_by(Dimension) %>%  arrange(Dimension,desc(`Loss (in %)`))
# 
# unit_no <- t %>% filter(unit == "Number of fish") %>% filter(Dimension %in% c("species", "source_authority","cat_geo", "fishingfleet", "species_group")) %>% mutate(Dimension = as.factor(Dimension)) %>%  group_by( Dimension) %>% arrange(desc(`Loss (in %)`))   %>%   mutate(id = row_number())%>%   mutate(test = as.factor(ifelse(id>(topn-1),paste0("Others"),paste0(as.character(Precision))))) %>% ungroup() %>% group_by(Dimension,test) %>% summarise(across(is.numeric, sum)) %>% mutate(`Loss (in %)` = (`Loss in millions of tons`*1000000/value_sum_1)*100) %>% select(-id)%>%group_by(Dimension) %>%  arrange(Dimension,desc(`Loss (in %)`))

unit <- t %>% filter(Dimension %in% c("species", "source_authority","cat_geo", "fishingfleet", "species_group", "gear")) %>% mutate(Dimension = as.factor(Dimension)) %>%  group_by( Dimension, unit) %>% arrange(desc(`Loss (in %)`))   %>%   mutate(id = row_number())%>%   mutate(Precision = as.factor(ifelse(id>(topn-1),paste0("Others"),paste0(as.character(Precision))))) %>% ungroup() %>% group_by(Dimension,Precision, unit) %>% summarise(across(is.numeric, sum)) %>% mutate(`Loss (in %)` = (`Loss in millions of tons`*1000000/value_sum_1)*100) %>% select(-id, -number_lines2)%>%group_by(unit,Dimension) %>%  arrange(Dimension,desc(`Loss (in %)`))

# %>% ungroup()%>% group_by(test,Dimension) %>% mutate_all(sum) %>% ungroup() %>% mutate(`Loss (in %)` =`Loss in millions of tons`/sum(`Loss in millions of tons`)) %>% mutate(Precision = test) %>%  mutate_if(is.character, as.factor)%>%select(-c(test,id)) %>%  group_by(Dimension) %>%arrange(Dimension,desc(`Loss (in %)`))

# unit_no <- t %>% filter(unit == "Number of fish") %>% filter(Dimension %in% c("species", "source_authority","cat_geo", "fishingfleet")) %>% mutate(Dimension = as.factor(Dimension)) %>%  mutate(test = ifelse(`Loss (in %)` >10,"Others",as.character(Precision))) %>%mutate(Precision = test) %>%    mutate(Perte_pourcent = 100*((value_sum_1 - value_sum_2)/value_sum_1)) %>%  mutate_if(is.character, as.factor)%>%select(-test) %>% ungroup() %>%  group_by(Precision,unit, Dimension)%>% summarise_all(sum)  %>% group_by(unit, Dimension) %>%arrange(desc(`Loss (in %)`), desc(`Loss in millions of tons`)) %>% group_by(Dimension)
# library(kable)
```


```{r paged.print=TRUE}
qflextable(as_grouped_data(unit %>% ungroup(), groups = c("Dimension","unit"))) 
```

What's missing in the smaller

```{r}

missing_small <- setdiff(final %>% select(-value), init%>% select(-value)) #%>% filter(gear %in% c("09.1" , "09.2" , "01.1" , "01.2" ))

lost_small <- setdiff(final, init)#%>% filter(gear %in% c("09.1" , "09.2" , "01.1" , "01.2" ))

missing_big <- setdiff(init %>% select(-value), final%>% select(-value))#%>% filter(gear %in% c("09.1" , "09.2" , "01.1" , "01.2" ))
params$init
```

