---
title: "Comparison raising shark and billfish"
output:
  html_document: default
  word_document: default
date: '2022-03-23'
---

This document give a quick analysis of the difference imputed to the raising of shark and billfish in IATCC data.

It explains the treatment and provide for each option choosen the differences on the final dataset.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE
)
library(readtext)
library(flextable)
set_flextable_defaults(
  font.size = 30,
  font.color = "black",
  table.layout = "fixed",
  digits = NULL,
  theme_fun = "theme_box"
  )
options(scipen=999)
library(dplyr)
library(stringr)
library(readr)
library(webshot)
if(require("htmltools"))
div(flextable_html_dependency())
pie_chart_2 = function(x, init= init,final = final) {
  r <- deparse(substitute(x))
  colnames <- enquo(x)
  provisoire_i <-init %>%  group_by(!!colnames, unit)%>% summarise(value = sum(value, na.rm = TRUE)) %>% group_by(unit) %>% arrange(desc(value)) %>%   mutate(id = row_number())%>%  
    mutate(class = as.factor(ifelse(id<4,!!colnames,"Others"))) %>%
    group_by(class, unit) %>%  summarise(value = sum(value, na.rm = TRUE))%>%ungroup()%>% 
    select(unit, value, class) %>%   group_by(unit) %>% mutate(pourcentage = prop.table(value)*100)%>%
    mutate(labels = paste0(pourcentage," ",  " % "))%>% arrange(desc(class))%>%
  mutate(ypos_ligne = cumsum(pourcentage)- 0.5*pourcentage ) %>%
    distinct()
  
  provisoire_t <- final %>%  group_by(!!colnames, unit)%>% summarise(value = sum(value, na.rm = TRUE)) %>% group_by(unit) %>% arrange(desc(value)) %>%   mutate(id = row_number())%>%  
    mutate(class = as.factor(ifelse(id<4,!!colnames,"Others"))) %>%
    group_by(class, unit) %>%  summarise(value = sum(value, na.rm = TRUE))%>%ungroup()%>% 
    select(unit, value, class) %>%   group_by(unit) %>% mutate(pourcentage = prop.table(value)*100)%>%
    mutate(labels = paste0(pourcentage," ",  " % "))%>% arrange(desc(class))%>%
  mutate(ypos_ligne = cumsum(pourcentage)- 0.5*pourcentage ) %>%
    distinct()
  
ggplot_i <- ggplot(provisoire_i) +
  aes(
    x = "",
    fill = class,
    colour = class,
    group = class,
    weight = pourcentage
  ) +
  geom_bar(position = "fill") +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  theme_minimal()+ coord_polar("y", start=0)+ geom_text(data = (provisoire_i %>% mutate_if(is.numeric, round)), size = 3,
                           aes( x = 1 ,y = ypos_ligne/100, label = paste0(pourcentage,"%")), color = "black")+
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())+
  labs(x = "", y="") + facet_wrap("unit")
  
ggplot_t <- ggplot(provisoire_t) +
  aes(
    x = "",
    fill = class,
    colour = class,
    group = class,
    weight = pourcentage
  ) +
  geom_bar(position = "fill") +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  theme_minimal()+ coord_polar("y", start=0)+ geom_text(data = (provisoire_t %>% mutate_if(is.numeric, round)), size = 3,
                           aes( x = 1, y = ypos_ligne/100, label = paste0(pourcentage,"%")), color = "black")+
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())+
  labs(x = "", y="") + facet_wrap("unit")

title <- ggdraw() + 
  draw_label(
    paste0("Distribution in value for the dimension : ",r),
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

graph <- plot_grid(ggplot_i, ggplot_t,nrow = 2,labels = c(paste0( titre_1), paste0(titre_2)),
  label_size = 10)

plot_grid(
  title, graph,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1))+
    theme(plot.background = element_rect(color = "black"))


}

```

```{r}
raising_shark <- readRDS("data/mapping_codelist.rds")
not_raising_shark <- readRDS("data/not_raising_shark_global_mapping_codelist.rds")
t <- setdiff(raising_shark, not_raising_shark)
raising_species <- unique(t$species)
```

# With raising shark version

For now, what is done is to raise the catches of sharks and billfishes in IATTC data and only in this one. Indeed, the catch is only give by the on-board observers. However they are not present on all the boat. What is done is to raise the catches of the species by the ratio effort/catches for tunas. 

# Without raising shark options

```{r}
comp <- gdata::combine(raising_shark, not_raising_shark)
comp$unit <- str_replace(comp$unit, "MTNO","MT")
comp$unit <- str_replace(comp$unit, "NOMT","NO")
comp <-  comp%>% group_by(source, time_start, unit) %>% summarise(Value = sum(value)) %>% mutate(time_start = as.Date(time_start)) 
```


```{r}
library(lubridate)
comp_year <- comp %>% mutate(Year =lubridate::year(time_start)) %>%ungroup() %>%  group_by(Year, unit, source) %>% summarise(Value = sum(Value))
```
```{r}
library(ggplot2)

ggplot(comp_year)+
  aes(x = Year, y = Value, colour = source) +
  geom_line(size = 0.5) +
  scale_color_hue(direction = 1) +
  theme_minimal() +
  facet_wrap(vars(unit), scales = "free_y")
```



The difference between the two dataset is `r sum((raising_shark %>% filter(unit == "MT"))$value) - sum((not_raising_shark %>% filter(unit == "MT"))$value)` in tons and `r sum((raising_shark %>% filter(unit == "NO"))$value) - sum((not_raising_shark %>% filter(unit == "NO"))$value)` in number of fish.

# Filtered on the concerned species

```{r}
# My treatment

not_raising_shark <- not_raising_shark %>% filter(species %in%raising_species)
raising_shark <- raising_shark %>% filter(species %in%raising_species)

```


```{r}
comp <- gdata::combine(raising_shark, not_raising_shark)
comp$unit <- str_replace(comp$unit, "MTNO","MT")
comp$unit <- str_replace(comp$unit, "NOMT","NO")
comp <-  comp%>% group_by(source, time_start, unit) %>% summarise(Value = sum(value)) %>% mutate(time_start = as.Date(time_start))
```

```{r}

comp_year <- comp %>% mutate(Year =lubridate::year(time_start)) %>%ungroup() %>%  group_by(Year, unit, source) %>% summarise(Value = sum(Value))
ggplot(comp_year)+
  aes(x = Year, y = Value, colour = source) +
  geom_line(size = 0.5) +
  scale_color_hue(direction = 1) +
  theme_minimal() +
  facet_wrap(vars(unit), scales = "free_y")
```

The difference between the two dataset is `r sum((raising_shark %>% filter(unit == "MT"))$value) - sum((not_raising_shark %>% filter(unit == "MT"))$value)` in tons and `r sum((raising_shark %>% filter(unit == "NO"))$value) - sum((not_raising_shark %>% filter(unit == "NO"))$value)` in number of fish.

```{r}
setdiff_raise <- setdiff(raising_shark, not_raising_shark)
setdiff_not_raise <- setdiff(not_raising_shark,raising_shark)
```


```{r}
titre_2 <- 'Not raised'
t <- pie_chart_2(species, setdiff_raise, setdiff_not_raise)
t
```

