---
title: "Etude de l'overlap"
output: html_document
date: '2022-03-14'
params:
  chemin_dacces: "~/Documents/Tunaatlas_level1/jobs/lastoneeeeeeeeeeeeeeeeeeee/entities/global_catch_1deg_1m_Bastien_include_wcpfc_level0/Markdown/mapping_codelist/rds.rds"
  plotting: "view"
  world_coastline: "gshhs_world_coastlines"
---

```{r setup, include=FALSE}
#data/Les7entites_finies/entities/global_catch_5deg_1m_firms_level0/Rds/georef_dataset_level0_step11global_catch_5deg_1m_firms_level0.rds"
#data/Les7entites_finies/entities/5deg_level1_reallocate/georef_dataset_step5.rds"
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(DBI)
library(RPostgres)
library(RPostgreSQL)
library(tmap)
library(dplyr, warn.conflicts = FALSE)
library(sf)
library(tmap)
library(tidyverse)
library(leaflet.minicharts)

```


```{r}

data <- readRDS(params$chemin_dacces)
  data <- data%>% mutate(unit = case_when(unit %in% c("MT","t","MTNO", "Tons")~ "Tons", unit %in% c("no", "NOMT", "Number of fish", "NO")~"Number of fish"))
cl_cwp_gear_level2 <- read_csv("data/cl_cwp_gear_level2.csv", 
    col_types = cols(Identifier = col_skip(), 
        Abbreviation = col_skip(), Name_Fr = col_skip(), 
        Name_Es = col_skip(), Name_Ar = col_skip()))

data <- data %>% full_join(cl_cwp_gear_level2, by = c("gear" = "Code"))

drv <- dbDriver("PostgreSQL")      
con <- DBI::dbConnect(drv , dbname = "tunaatlas", host = "db-tunaatlas.d4science.org", 
                      port = 5432,
                      user = "tunaatlas_u",
                      password = "21c0551e7ed2911")


query <- "SELECT  code,st_area(geom), geom from area.cwp_grid"
world_sf <- st_make_valid(st_read(con, query = query))%>% filter(!st_is_empty(.))

query_area <- paste0("SELECT * FROM area.rfmos_convention_areas_fao")
competence_area <- st_make_valid(st_read(con, query = query_area)) %>% filter(!st_is_empty(.))
IOTC_shape <- competence_area %>% filter(code == "IOTC")
IATTC_shape <- competence_area %>% filter(code == "IATTC")
WCPFC_shape <- competence_area %>% filter(code == "WCPFC")
ICCAT_shape <- competence_area %>% filter(code == "ICCAT")
query <- "SELECT  code,st_area(geom), geom from area.gshhs_world_coastlines"
continent <- st_read(con, query = query)%>% filter(!st_is_empty(.))
query <- "SELECT  code,code_cwp,st_area(geom), geom from area.irregular_areas_task2_iotc"
irregular_iotc <- st_read(con, query = query)%>% filter(!st_is_empty(.))
irregular_iotc <-irregular_iotc  %>% distinct()
# test <- data %>% inner_join(irregular_iotc %>% st_set_geometry(NULL) , by = c("geographic_identifier"= "code")) %>% mutate(geographic_identifier = code_cwp)
irregular_iotc[irregular_iotc$code_cwp =="1100030",]$code_cwp <- "9100030"
irregular_iotc[irregular_iotc$code_cwp =="2120060",]$code_cwp <- "8120060"
irregular_iotc[irregular_iotc$code_cwp =="3200050",]$code_cwp <- "7200050"
if(any(irregular_iotc$code_cwp =="4220040")) irregular_iotc[irregular_iotc$code_cwp =="4220040",]$code_cwp <- "8220040"

world_sf <- world_sf %>% mutate(code_cwp = code)

tmap_mode("view")
# tm_shape(st_as_sf(test %>% inner_join(world_sf, by = c("geographic_identifier" = "code"))))+tm_polygons()
pakistan <- irregular_iotc %>% filter(code_cwp== "3120060")
world_sf_combined <- rbind(pakistan, world_sf)
# world_sf_combined <- gdata::combine(world_sf, irregular_iotc) %>% distinct()
# t <- rbind(world_sf_combined[duplicated(world_sf_combined$code_cwp),],world_sf_combined[duplicated(world_sf_combined$code_cwp, fromLast = TRUE),] )

data <- left_join(data, irregular_iotc %>% st_set_geometry(NULL), by =c("geographic_identifier"= "code")) %>% mutate(geographic_identifier= ifelse(!is.na(code_cwp), code_cwp, geographic_identifier)) %>% select(-c(code_cwp, st_area))

# testtt <- setdiff(irregular_iotc$code_cwp, world_sf$code_cwp)
# 
# test <- t %>% group_by(code, source) %>% slice(1)
# tm_shape(st_as_sf(t))+tm_polygons()+tm_fill(col = "source")
# 
IOTC <- world_sf[IOTC_shape,]%>% st_set_geometry(NULL) %>% mutate(iotc = "iotc")

IATTC <- world_sf[IATTC_shape,]%>% st_set_geometry(NULL) %>% mutate(iattc = "iattc")

WCPFC <- world_sf[WCPFC_shape,]%>% st_set_geometry(NULL) %>% mutate(wcpfc = "wcpfc")

ICCAT <- world_sf[ICCAT_shape,]%>% st_set_geometry(NULL) %>% mutate(iccat = "iccat")



full_join <- full_join(full_join(full_join(full_join(world_sf, IOTC), IATTC), WCPFC), ICCAT) %>% st_set_geometry(NULL) 


full_join[is.na(full_join)] <-  FALSE

full_join <- full_join %>% mutate(area_competence = as.factor(gsub("FALSE","",paste0(iotc, iattc, wcpfc, iccat))))
world_sf$continent <- st_within(world_sf, continent) %>% lengths > 0 
world_sf$continent <- str_replace(world_sf$continent, "TRUE","continent")

world_sf <- left_join(world_sf, full_join)

world_sf_with_competence_area <- world_sf %>% mutate(area_competence = as.factor(gsub("FALSE","",paste0(iotc, iattc, wcpfc, iccat, continent))))


inner_join <- data %>% inner_join(world_sf_with_competence_area, by = c("geographic_identifier"="code"))



all_the_data <- inner_join  %>% ungroup() %>% group_by(geographic_identifier, st_area, unit, source_authority, area_competence) %>% summarise(value= sum(value, na.rm = TRUE))%>% distinct() %>% inner_join(world_sf%>% select(-area_competence) , by = c("geographic_identifier"="code", "st_area") ) %>% select(geographic_identifier, st_area, value, geom, unit, source_authority, area_competence)

mislocated_continent <- all_the_data %>% filter(str_detect(area_competence, "continent"))
if (nrow(mislocated_continent)==0){knitr::knit_exit()}else{
tmap_mode(params$plotting)

tm_shape(st_as_sf(mislocated_continent %>% mutate(st_area = as.factor(st_area))))+tm_fill("value")+tm_facets(by=c("st_area","unit"))+tm_text("source_authority")#+tm_shape(continent)+tm_borders() 

}


```

# Distribution of mislocated data 

```{r}

mislocated_continent2 <- mislocated_continent %>% group_by(unit, source_authority) %>% arrange(unit,desc(source_authority)) %>% summarise(value = sum(value, na.rm = TRUE))  %>% ungroup() %>% group_by(unit) %>%  mutate(pourcentage = prop.table(value)*100)%>%
    mutate(labels = paste0(pourcentage," ",  " % "))%>% arrange(unit,desc( source_authority)) %>% 
  mutate(ypos_ligne = cumsum(pourcentage)- 0.5*pourcentage ) %>%
    distinct()
ggplot(mislocated_continent2) +aes(
    x = "",
    fill = source_authority,
    colour = source_authority,
    group = source_authority,
    weight = pourcentage
  ) +
  geom_bar(position = "fill") +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  theme_minimal()+ coord_polar("y", start=0)+ geom_text(data = (mislocated_continent2 %>% mutate_if(is.numeric, round)), size = 3,
                           aes( x = 1 ,y = ypos_ligne/100, label = paste0(pourcentage,"%")), color = "black")+
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())+
  labs(x = "", y="") + facet_wrap("unit")

```


***This markdown is aimed to study the repartition of each unity for a specific dataset, in this case is `r params$chemin_dacces`.***

```{r}
all_the_data3 <- all_the_data %>% mutate(continent = ifelse(area_competence != "continent", "ocean", "continent"))

```


```{r}
# st_geometry(all_the_data3) <- NULL
final <- all_the_data3 %>% group_by(continent, unit) %>% summarise(value = sum(value))
# all_the_data2_without_continent <- all_the_data %>% filter(area_competence != "continent")
# value_without_continent <- sum(all_the_data2_without_continent$value, na.rm =TRUE)

en_nombre_continent <- pull(final %>% filter(unit == "Number of fish") %>% filter(continent == "continent"))
en_nombre_ocean <- pull(final %>% filter(unit == "Number of fish") %>% filter(continent == "ocean"))
en_tonne_continent <- pull(final %>% filter(unit == "Tons") %>% filter(continent == "continent"))
en_tonne_ocean <- pull(final %>% filter(unit == "Tons") %>% filter(continent == "ocean"))

perte_en_nombre <- (en_nombre_continent / (en_nombre_ocean+en_nombre_continent))*100
perte_en_tonne <- (en_tonne_continent/ (en_tonne_continent+en_tonne_ocean))*100

# value_with_continent <- sum(all_the_data$value, na.rm = TRUE)

# perte_en_pourcent_conitnent <- ((value_with_continent-value_without_continent)/value_with_continent)*100
```

Removing the data placed on the continents, the losses at the end of level 0 amount to `r perte_en_nombre` % in number and `r perte_en_tonne` % in tons. 

We are now interested in the mislocated data

```{r}

# mislocated <- inner_join %>%filter(!str_detect(area_competence, "continent")) %>%  ungroup() %>% select(area_competence, source_authority, value, unit, geom) %>% mutate(area_competence = toupper(area_competence)) %>%  mutate(mislocated = case_when(source_authority =="CCSBT" ~TRUE, area_competence%in%c("IATTC", "ICCAT", "IOTC", "WCPFC") & area_competence == source_authority ~ TRUE,
#                               area_competence == "IOTCWCPFC" & source_authority %in% c("IOTC", "WCPFC")  ~ TRUE,
#                               area_competence == "IATTCWCPFC" & source_authority %in% c("IATTC", "WCPFC")  ~ TRUE, tolower(area_competence) == area_competence ~ TRUE, 
#                               TRUE ~ FALSE))

mislocated <- inner_join %>% mutate(area_competence = as.character(area_competence)) %>% filter(!str_detect(inner_join$area_competence, "continent")) %>% filter(!is.null(area_competence))%>% filter(area_competence != "")%>% mutate(area_competence= as.factor(area_competence)) %>%  ungroup() %>% select(area_competence, source_authority, value, unit, geom) %>% mutate(source_authority = tolower(source_authority)) %>%  mutate(mislocated = case_when(str_detect(area_competence, source_authority) == TRUE ~ TRUE, area_competence == source_authority ~ TRUE, source_authority == "CCSBT"~TRUE,
                              TRUE ~ FALSE))

final <- mislocated %>% group_by(mislocated, unit) %>% summarise(value = sum(value))
en_nombre_false<- pull(final %>% filter(unit == "Number of fish") %>% filter(mislocated == FALSE))
en_nombre_true <- pull(final %>% filter(unit == "Number of fish") %>% filter(mislocated == TRUE))
en_tonne_false <- pull(final %>% filter(unit == "Tons") %>% filter(mislocated == FALSE))
en_tonne_true <- pull(final %>% filter(unit == "Tons") %>% filter(mislocated == TRUE))

perte_en_nombre <- (en_nombre_false / (en_nombre_true+en_nombre_false))*100
perte_en_tonne <- (en_tonne_false/ (en_tonne_false+en_tonne_true))*100


```

```{r eval=FALSE}
# tm_shape(IOTC)+tm_fill(alpha = 0.2, col = "red")+tm_shape(IATTC)+tm_fill(alpha = 0.2, col = "yellow")+tm_shape(ICCAT)+tm_fill(alpha = 0.2, col = "purple")+tm_shape(WCPFC)+tm_fill(alpha = 0.2, col = "skyblue")+tm_shape(st_as_sf(mislocated %>% filter(mislocated ==FALSE) %>% filter(source_authority!="CCSBT")))+tm_polygons(col = "source_authority")+tm_facets("unit")
```

```{r}
tm_shape(WCPFC_shape %>% mutate(name = "WCPFC"))+tm_borders( col = "red")+tm_text("name")+tm_shape(ICCAT_shape%>% mutate(name = "ICCAT"))+tm_borders( col = "yellow")+tm_text("name")+tm_shape(IOTC_shape%>% mutate(name = "IOTC"))+tm_borders( col = "purple")+tm_text("name")+tm_shape(IATTC_shape%>% mutate(name = "IATTC"))+tm_borders( col = "skyblue")+tm_text("name")+tm_shape(st_as_sf(mislocated %>% filter(mislocated ==FALSE) %>% filter(source_authority!="ccsbt") %>%  filter(area_competence != "") %>% filter(!is.null(area_competence))))+tm_polygons(col = "source_authority")+tm_text("source_authority")+tm_facets("unit")

```


Removing data placed on continents, as well as data from an rfmo in an area outside their jurisdiction, the losses at the end of level 0 amount to `r perte_en_nombre` % in number and `r perte_en_tonne` % in tons. 
 
## Study of overlapping zones

Regarding the areas where there is more than one RFMO giving information, we need to choose a way to handle the data. 

First we will describe the data of those areas and after we will provide the choice apropriate.

### Brief description of overlapping data

We consider only the overlap IOTC/WCPFC and the IATTC/WCPFC and the IATTC/ICCAT, the overlaps concerning the CCSBT we'll be handle differently. 

```{r}
overlapping_without_ccsbt <- inner_join %>% filter(area_competence %in% c("iotcwcpfc", "iattcwcpfc", "iattciccat", "iotciccat")) %>% filter(source_authority != "CCSBT")
```

```{r}
tilesURL = "http://server.arcgisonline.com/ArcGIS/rest/services/Canvas/World_Light_Gray_Base/MapServer/tile/{z}/{y}/{x}"
library(leaflet.minicharts)
library(leaflet)
basemap = leaflet(width = "100%", height = "800px") %>%
  addTiles(tilesURL)
regions <-  c("IOTC", "WCPFC", "ICCAT", "IATTC")
```


```{r}
t <- st_as_sf(overlapping_without_ccsbt%>% group_by(unit,geographic_identifier, source_authority) %>% summarise(value = sum(value, na.rm = TRUE))%>% pivot_wider(names_from = source_authority, values_from = value, values_fill = 0) %>% ungroup() %>% inner_join(world_sf, by = c("geographic_identifier"="code"))) %>% 
  st_transform(4326)
t_no <- t %>% filter(unit == "Number of fish")
t_tons <- t %>% filter(unit == "Tons")
region.tb_no = t_no  %>% 
  st_point_on_surface() %>% 
  st_coordinates() %>% 
  as_tibble() %>% 
  rename(lon = 1, lat = 2) %>% 
  bind_cols(t_no %>% st_drop_geometry()) %>% 
  mutate(total = IOTC + IATTC+ WCPFC + ICCAT)
region.tb_tons = t_tons  %>% 
  st_point_on_surface() %>% 
  st_coordinates() %>% 
  as_tibble() %>% 
  rename(lon = 1, lat = 2) %>% 
  bind_cols(t_tons %>% st_drop_geometry()) %>% 
  mutate(total = IOTC + IATTC+ WCPFC + ICCAT)
```

In number of fish

```{r}
basemap  %>%
  addMinicharts(lng = region.tb_no$lon, 
                lat = region.tb_no$lat, 
                type = "pie", 
                chartdata = region.tb_no[,regions], 
             
                width = 60 * sqrt(region.tb_no$total) / sqrt(max(region.tb_no$total)), 
                transitionTime = 0) 
```

In tons 

```{r}

basemap  %>%
  addMinicharts(lng = region.tb_tons$lon, 
                lat = region.tb_tons$lat, 
                type = "pie", 
                chartdata = region.tb_tons[,regions], 
             
                width = 60 * sqrt(region.tb_tons$total) / sqrt(max(region.tb_tons$total)), 
                transitionTime = 0) 
```



```{r}
count_na_func <- function(x) sum(is.na(x))



differenciate_area_unique_autho_area_multiple <- st_as_sf(overlapping_without_ccsbt%>% group_by(unit,geographic_identifier, source_authority) %>% summarise(value = sum(value, na.rm = TRUE))%>% pivot_wider(names_from = source_authority, values_from = value) %>% ungroup() %>% inner_join(world_sf, by = c("geographic_identifier"="code"))) %>% 
  st_transform(4326)
st_geometry(differenciate_area_unique_autho_area_multiple) <- NULL
  differenciate_area_unique_autho_area_multiple <- differenciate_area_unique_autho_area_multiple %>% mutate(count_na = apply(., 1, count_na_func)) %>% 
mutate(From_where =case_when(count_na == 3 ~ "Only data from one source authority", TRUE~ "Data from multiple source authority"))  %>%  rowwise() %>% 
  mutate(value = sum(c_across(c("IOTC", "WCPFC", "ICCAT", "IATTC")), na.rm = T))

recap_multpile_unique_SA <- differenciate_area_unique_autho_area_multiple %>% group_by(unit,From_where) %>% summarise(nrow = n() ,value = sum(value, na.rm = TRUE))

```


```{r}
table <- recap_multpile_unique_SA%>% mutate(pourcentage_value = prop.table(value)*100, pourcentage_row = prop.table(nrow)*100)%>%
    mutate(labels_value = paste0(round(pourcentage_value),"  % "),
                                 labels_row = paste0(round(pourcentage_row),"  % "))%>%  ungroup() %>% group_by(unit) %>%arrange(unit,desc(pourcentage_value)) %>%  
  mutate(ypos_ligne_value = cumsum(pourcentage_value)- 0.5*pourcentage_value) %>% ungroup() %>% group_by(unit) %>%arrange(unit,desc(pourcentage_row)) %>% mutate(ypos_ligne_row =  cumsum(pourcentage_row)- 0.5*pourcentage_row ) %>%
    distinct()
```


```{r}
value <- ggplot(table) +
  aes(
    x = "",
    fill = From_where,
    colour = From_where,
    group = From_where,
    weight = pourcentage_value
  ) +
  geom_bar(position = "fill") +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  theme_minimal()+ coord_polar("y", start=0)+ geom_text(data = (table %>% mutate_if(is.numeric, round)), size = 3,
                           aes( x = 1 ,y = ypos_ligne_value/100, label = paste0(pourcentage_value,"%")), color = "black")+
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())+
  labs(x = "", y="", title = "In value") +facet_wrap("unit")


```

```{r paged.print=TRUE}
row <- ggplot(table) +
  aes(
    x = "",
    fill = From_where,
    colour = From_where,
    group = From_where,
    weight = pourcentage_row
  ) +
  geom_bar(position = "fill") +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  theme_minimal()+ coord_polar("y", start=0)+ geom_text(data = (table %>% mutate_if(is.numeric, round)), size = 3,
                           aes( x = 1 ,y = ypos_ligne_row/100, label = paste0(pourcentage_row,"%")), color = "black")+
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())+
  labs(x = "", y="", title = "In rows") +facet_wrap("unit")
value
row
```

## Data from multiple sources

We only analyse the data where two differents RFMOs coexist on the same geographic identifier first

```{r}
data_where_overlap <- differenciate_area_unique_autho_area_multiple
# st_geometry(data_where_overlap) <- NULL
data_where_overlap <- data_where_overlap %>% filter(From_where == "Data from multiple source authority")%>% group_by(unit,geographic_identifier, area_competence) %>% arrange(desc(value)) %>%  distinct()
data_where_overlap[is.na(data_where_overlap)] <-  0
t <- st_as_sf(data_where_overlap %>% inner_join(world_sf %>% select(code), by = c( "geographic_identifier"="code")))
region.tb =  t%>% 
  st_point_on_surface() %>% 
  st_coordinates() %>% 
  as_tibble() %>% 
  rename(lon = 1, lat = 2) %>% 
  bind_cols(t %>% st_drop_geometry()) %>% 
  mutate(total = IOTC + IATTC+ WCPFC + ICCAT)

tilesURL = "http://server.arcgisonline.com/ArcGIS/rest/services/Canvas/World_Light_Gray_Base/MapServer/tile/{z}/{y}/{x}"
library(leaflet.minicharts)
library(leaflet)
basemap = leaflet(width = "100%", height = "800px") %>%
  addTiles(tilesURL)

basemap  %>%
  addMinicharts(lng = region.tb$lon, 
                lat = region.tb$lat, 
                type = "pie", 
                chartdata = region.tb[, c("IOTC", "WCPFC", "ICCAT", "IATTC")], 
               
                width = 60 * sqrt(region.tb$total) / sqrt(max(region.tb$total)), 
                transitionTime = 0) 

```

```{r}
data_where_overlap_with_all_informations <- inner_join(data, data_where_overlap %>%ungroup() %>%  select(geographic_identifier,st_area, area_competence), by = "geographic_identifier") %>% mutate(time_start = as.Date(time_start), time_end = as.Date(time_end))
```

```{r}
ggplot(data_where_overlap_with_all_informations %>% group_by(unit,time_start, source_authority, area_competence) %>% summarise(value = sum(value, na.rm = TRUE)) %>%  filter(source_authority != "CCSBT")) +
  aes(x = time_start, y = value, colour = source_authority) +
  geom_line(size = 0.5) +
  scale_color_hue(direction = 1) +
  theme_minimal() +
  facet_wrap(vars(unit,area_competence), scales = "free_y")
```


```{r}
library(readr)
library(readxl)
species_group <-  read_excel("data/SPECIES_LIST_RFMO_WITH_ERRORS.xlsx") %>% janitor::clean_names() %>%  select(species_group, species_code) %>% rename(species = species_code)
data_where_overlap_with_all_informations <- data_where_overlap_with_all_informations%>% inner_join(species_group, by = c("species"))%>% mutate(cat_geo = as.factor(case_when(st_area == 1 ~ "1_deg", st_area == 25 ~ "5_deg", TRUE ~ ">_5_deg")))

```

```{r}
ggplot(data_where_overlap_with_all_informations %>% group_by(unit,species_group, source_authority, area_competence) %>% summarise(value = sum(value, na.rm = TRUE)) %>% filter(source_authority != "CCSBT")) +
  aes(
    x = species_group,
    colour = source_authority,
    weight = value
  ) +
  geom_bar(fill = "#112446") +
  scale_color_hue(direction = 1) +
  coord_flip() +
  theme_minimal() +
  facet_wrap(vars(unit,area_competence), scales = "free")
```

```{r}
ggplot(data_where_overlap_with_all_informations %>% group_by(unit,cat_geo, source_authority, area_competence) %>% summarise(value = sum(value, na.rm = TRUE)) %>% filter(source_authority != "CCSBT")) +
  aes(
    x = cat_geo,
    colour = source_authority,
    weight = value
  ) +
  geom_bar(fill = "#112446") +
  scale_color_hue(direction = 1) +
  coord_flip() +
  theme_minimal() +
  facet_wrap(vars(unit,area_competence), scales = "free")
```

```{r fig.asp = 0.8, fig.width = 10}
ggplot(data_where_overlap_with_all_informations %>% group_by(unit,gear, Name_En,source_authority, area_competence) %>% summarise(value = sum(value, na.rm = TRUE)) %>% filter(source_authority != "CCSBT")) +
  aes(
    x = Name_En,
    colour = source_authority,
    weight = value
  ) +
  geom_bar(fill = "#112446") +
  scale_color_hue(direction = 1) +
  coord_flip() +
  theme_minimal() +
  facet_wrap(vars(unit,area_competence), scales = "free")
```

## All data in overlap zones

We make now, the analysis on the complete dataset of overlapping zones.

```{r}
data_where_overlap <- differenciate_area_unique_autho_area_multiple
# st_geometry(data_where_overlap) <- NULL
data_where_overlap <- data_where_overlap %>% group_by(unit,geographic_identifier, area_competence) %>% arrange(desc(value)) %>%  distinct()
data_where_overlap[is.na(data_where_overlap)] <-  0
t <- st_as_sf(data_where_overlap %>% inner_join(world_sf %>% select(code), by = c( "geographic_identifier"="code")))
region.tb =  t%>% 
  st_point_on_surface() %>% 
  st_coordinates() %>% 
  as_tibble() %>% 
  rename(lon = 1, lat = 2) %>% 
  bind_cols(t %>% st_drop_geometry()) %>% 
  mutate(total = IOTC + IATTC+ WCPFC + ICCAT)

tilesURL = "http://server.arcgisonline.com/ArcGIS/rest/services/Canvas/World_Light_Gray_Base/MapServer/tile/{z}/{y}/{x}"
library(leaflet.minicharts)
library(leaflet)
basemap = leaflet(width = "100%", height = "800px") %>%
  addTiles(tilesURL)

basemap  %>%
  addMinicharts(lng = region.tb$lon, 
                lat = region.tb$lat, 
                type = "pie", 
                chartdata = region.tb[, c("IOTC", "WCPFC", "ICCAT", "IATTC")], 
               
                width = 60 * sqrt(region.tb$total) / sqrt(max(region.tb$total)), 
                transitionTime = 0) 

```

```{r}
data_where_overlap_with_all_informations <- inner_join(data, data_where_overlap %>%ungroup() %>%  select(geographic_identifier,st_area, area_competence), by = "geographic_identifier") %>% mutate(time_start = as.Date(time_start), time_end = as.Date(time_end))
```

```{r}
ggplot(data_where_overlap_with_all_informations %>% group_by(unit,time_start, source_authority, area_competence) %>% summarise(value = sum(value, na.rm = TRUE)) %>%  filter(source_authority != "CCSBT")) +
  aes(x = time_start, y = value, colour = source_authority) +
  geom_line(size = 0.5) +
  scale_color_hue(direction = 1) +
  theme_minimal() +
  facet_wrap(vars(unit,area_competence), scales = "free_y")
```


```{r}
library(readr)
library(readxl)
species_group <-  read_excel("data/SPECIES_LIST_RFMO_WITH_ERRORS.xlsx") %>% janitor::clean_names() %>%  select(species_group, species_code) %>% rename(species = species_code)
data_where_overlap_with_all_informations <- data_where_overlap_with_all_informations%>% inner_join(species_group, by = c("species"))%>% mutate(cat_geo = as.factor(case_when(st_area == 1 ~ "1_deg", st_area == 25 ~ "5_deg", TRUE ~ ">_5_deg")))

```

```{r}
ggplot(data_where_overlap_with_all_informations %>% group_by(unit,species_group, source_authority, area_competence) %>% summarise(value = sum(value, na.rm = TRUE)) %>% filter(source_authority != "CCSBT")) +
  aes(
    x = species_group,
    colour = source_authority,
    weight = value
  ) +
  geom_bar(fill = "#112446") +
  scale_color_hue(direction = 1) +
  coord_flip() +
  theme_minimal() +
  facet_wrap(vars(unit,area_competence), scales = "free")
```

```{r}
ggplot(data_where_overlap_with_all_informations %>% group_by(unit,cat_geo, source_authority, area_competence) %>% summarise(value = sum(value, na.rm = TRUE)) %>% filter(source_authority != "CCSBT")) +
  aes(
    x = cat_geo,
    colour = source_authority,
    weight = value
  ) +
  geom_bar(fill = "#112446") +
  scale_color_hue(direction = 1) +
  coord_flip() +
  theme_minimal() +
  facet_wrap(vars(unit,area_competence), scales = "free")
```

```{r}
ggplot(data_where_overlap_with_all_informations %>% group_by(unit,gear,Name_En, source_authority, area_competence) %>% summarise(value = sum(value, na.rm = TRUE)) %>% filter(source_authority != "CCSBT")) +
  aes(
    x = Name_En,
    colour = source_authority,
    weight = value
  ) +
  geom_bar(fill = "#112446") +
  scale_color_hue(direction = 1) +
  coord_flip() +
  theme_minimal() +
  facet_wrap(vars(unit,area_competence), scales = "free")
```


The definition of the CCSBT competence authority area is not yet provided. Ancient way was to suppress all the SBF data coming from another source authority than CCSBT. In this section we will study the distribution of SBF depending on various factors. 

## SBF data

### Distribution of SBF data 

```{r}
data_only_sbf <- data %>% filter(species == "SBF")
```

```{r}
ggplot(data_only_sbf) +
  aes(x = source_authority, weight = value) +
  geom_bar(fill = "#112446") +
  theme_minimal()
```

SBF captures are declared only by CCSBT. 

However they do not declare only SBF. 