---
title: "lancement de toutes les comparaisons"
author: "Bastien Grasset"
date: "09/02/2022"
output: html_document
params: 
  working_directory: "Les7entites_finies"
  strates_to_check_doublon: c("time_start", "species", "unit")

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(dplyr)
library(stringr)
```

```{r}
last_path = function(x){tail(str_split(x,"/")[[1]],n=1)}
last_path_reduced = function(x){gsub("georef_dataset","",last_path(x))}

fonction_markdown_si_diff = function(init, final,nom_de_sortie1 = last_path_reduced(init), nom_de_sortie2 = last_path_reduced(final)){
  init2 <- readRDS(init)
  final2 <- readRDS(final)
  if (!(identical(init2, final2))) {
    somme_init_t <- sum((init2 %>% filter(unit %in%c("t", "MT")))$value, na.rm = TRUE)
    somme_init_no <- sum((init2 %>% filter(unit %in%c("no", "NO")))$value, na.rm = TRUE)
    somme_final_t <- sum((final2 %>% filter(unit %in%c("t", "MT")))$value, na.rm = TRUE)
    somme_final_no <- sum((final2 %>% filter(unit %in%c("no", "NO")))$value, na.rm = TRUE)
    
    print(paste0("Le jeux de données initial a un total de ",round(somme_init_t), " en tonnes et de ",round(somme_init_no)," en nombre de poisson."))
    
    print(paste0("Le jeux de données final a un total de ",round(somme_final_t), " en tonnes et de ",round(somme_final_no)," en nombre de poisson."))
    perte_en_tonnes <- round(somme_init_t-somme_final_t)
    perte_en_tonnes_pourcent <- round(100*(somme_init_t-somme_final_t)/somme_init_t,2)
    perte_en_nombre <- round(somme_init_no-somme_final_no)
    perte_en_nombre_pourcent <- round(100*(somme_init_no-somme_final_no)/somme_init_no,2)
    
    print(paste0("La perte en tonnes est de ", perte_en_tonnes, "(", perte_en_tonnes_pourcent, "% )", "la perte en nombre est de ", perte_en_nombre, "(", perte_en_nombre_pourcent, "% )"))
    
   if(!(exists(paste0("Markdown/",nom_de_sortie1,"comp",nom_de_sortie1,".html")))){
    
      rmarkdown::render("comp_sans_shiny.Rmd", params = list(init = init, final = final), output_file  = paste0("Markdown/",nom_de_sortie1,"comp",nom_de_sortie1,".html"))
    # print(paste0("Nous pouvons retrouver la comparaison détaillée des deux jeux de données sous le chemin d'accès Markdown/",last_path_reduced(init),"comp",last_path_reduced(final),".html"))

      
    }
        
      
    
  } else {print(paste0("There are no differences between", last_path_reduced(init), "and", last_path_reduced(final)))}
  rm(list=ls()[ends_with(".rds", vars=ls())])
gc()
}
```

The purpose of this markdown is to run all the comparisons between the data from the tunaatlas run. 

The comparisons are done two by two between each dataset and we will be particularly interested in some variables of interest depending on the datasets used. 

First we run all comparisons between the initial and final data of each entity. Then we compare the final data between them and finally we will be interested in the impact of the different steps for each entity. 
Finally in a last step and possibly another markdown, we will study within each entity some losses for some steps. 

# Comparison of initial and final data for each entity

```{r}
library(RMySQL)
library(stringr)
fonction_markdown_si_diff_init = function(init, final,nom_de_sortie1 = init, nom_de_sortie2 = final,i){
  init2 <- readRDS(paste0(i,"/Rds/",init))
  final2 <- readRDS(paste0(i,"/Rds/",final))
    if (!(identical(init2, final2))) {
    somme_init_t <- sum((init2 %>% filter(unit %in%c("t", "MT")))$value, na.rm = TRUE)
    somme_init_no <- sum((init2 %>% filter(unit %in%c("no", "NO")))$value, na.rm = TRUE)
    somme_final_t <- sum((final2 %>% filter(unit %in%c("t", "MT")))$value, na.rm = TRUE)
    somme_final_no <- sum((final2 %>% filter(unit %in%c("no", "NO")))$value, na.rm = TRUE)
    
    print(paste0("Le jeux de données initial a un total de ",round(somme_init_t), " en tonnes et de ",round(somme_init_no)," en nombre de poisson."))
    
    print(paste0("Le jeux de données final a un total de ",round(somme_final_t), " en tonnes et de ",round(somme_final_no)," en nombre de poisson."))
    perte_en_tonnes <- round(somme_init_t-somme_final_t)
    perte_en_tonnes_pourcent <- round(100*(somme_init_t-somme_final_t)/somme_init_t,2)
    perte_en_nombre <- round(somme_init_no-somme_final_no)
    perte_en_nombre_pourcent <- round(100*(somme_init_no-somme_final_no)/somme_init_no,2)
    
    print(paste0("La perte en tonnes est de ", perte_en_tonnes, " (", perte_en_tonnes_pourcent, "%)", "la perte en nombre est de ", perte_en_nombre, " (", perte_en_nombre_pourcent, "%)"))
   if(!(exists(paste0("Markdown/",last_path_reduced(init),"comp",last_path_reduced(final),".html")))){

      rmarkdown::render("comp_sans_shiny.Rmd", params = list(init = paste0(i,"/Rds/",init), final = paste0(i,"/Rds/",final)), output_file  = paste0("Markdown/",last_path_reduced(init),"comp",last_path_reduced(final),".html"))
    # print(paste0("Nous pouvons retrouver la comparaison détaillée des deux jeux de données sous le chemin d'accès Markdown/", last_path_reduced(init),"comp",last_path_reduced(final),".html"))
     }
    
  } else {print(paste0("There are no differences between",last_path_reduced(init), "and", last_path_reduced(final)))}
  
}

list_dir <- list.dirs(path =paste0("data/",params$working_directory, "/entities"), full.names = TRUE, recursive = FALSE)
dir.create(paste0("data/",params$working_directory, "/entities","/Markdown"))

#only for this example

list_dir <- list_dir[c(2,5,7)]
# automatisation mais pas assez bien je pense
# list_dir <- list_dir[c(7)]
```


```{r}
#begin
for (i in list_dir){

  tmpshot <- fileSnapshot(paste0(i,"/Rds"))
init <- rownames(tmpshot$info[which.min(tmpshot$info$mtime),])
last <- rownames(tmpshot$info[which.max(tmpshot$info$mtime),])
fonction_markdown_si_diff_init(init, last, i= i)
rm(list=ls()[ends_with(".rds", vars=ls())])
gc()
}



```



# Comparison of the final data between them 

For these comparisons we will not compare all the datasets with each other, which would be very long and not very useful. We will only evaluate the difference between the principals and the nominals catches as well as the difference between the particular entities and their counterparts with one option more or less (include WCPFC or raise billshark)

# Comparison 1 degree total

```{r}
fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step11global_catch_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_1deg_1m_ps_bb_firms_level0/Rds/georef_dataset_level0_step11global_catch_1deg_1m_ps_bb_firms_level0.rds")
```

# Comparaison 5 degrés total

```{r}
fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step11global_catch_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_5deg_1m_ps_bb_firms_level0/Rds/georef_dataset_level0_step11global_catch_5deg_1m_ps_bb_firms_level0.rds")
```

# Analyse des options initiales

## Analyse de l'inclusion ou non de WCPFC sur les données 1 deg

```{r}
fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_1deg_1m_ps_bb_firms_level0/Rds/georef_dataset_level0_step11global_catch_1deg_1m_ps_bb_firms_level0.rds","data/Les7entites_finies/entities/global_catch_1deg_1m_ps_bb_includeWCPFC_firms_level0/Rds/georef_dataset_level0_step11global_catch_1deg_1m_ps_bb_includeWCPFC_firms_level0.rds", "without_wpcpf", "with_wcpfc")

  # rmarkdown::render("comp_sans_shiny.Rmd", params = list(init = "global_catch_1deg_1m_ps_bb_firms_level0/Rds/georef_dataset_level0_step11global_catch_1deg_1m_ps_bb_firms_level0", final ="global_catch_1deg_1m_ps_bb_options_raise_false_firms_level0/Rds/georef_dataset_level0_step11global_catch_1deg_1m_ps_bb_options_raise_false_firms_level0"), output_dir = paste0("comparaison_including_wcpfc",init,"final",final,"Markdown.html"))

```

We note that there is no difference between the 1 degree tuna atlas including or not the WCPFC data.

## Raising factor analysis on 1 deg shark IATTC data

```{r eval=FALSE, include=FALSE}

fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_1deg_1m_ps_bb_firms_level0/Rds/georef_dataset_level0_step11global_catch_1deg_1m_ps_bb_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_1deg_1m_ps_bb_options_raise_false_firms_level0/Rds/georef_dataset_level0_step11global_catch_1deg_1m_ps_bb_options_raise_false_firms_level0.rds", "withoutraising", "withraising")
  

```

## Analyse of raising factor on IATTC data for billfish/shark on 5 deg tunaatlas

```{r eval=FALSE, include=FALSE}
fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_5deg_1m_firms_level0/Rds/georef_dataset_level0_step11global_catch_5deg_1m_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_5deg_1m_firms_options_raise_false_level0/Rds/georef_dataset_level0_step11global_catch_5deg_1m_firms_options_raise_false_level0.rds", "withraising", "withoutraising")
```

## Analyse of raising factor on IATTC data for billfish/shark on global tunaatlas

```{r eval=FALSE, include=FALSE}
fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step11global_catch_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_firms_options_raise_false_level0/Rds/georef_dataset_level0_step11global_catch_firms_options_raise_false_level0.rds", "withraising", "withoutraising")
```

### Filtering on IATTC

```{r}
rmarkdown::render("comp_sans_shiny.Rmd", params = list(init = "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step11global_catch_firms_level0.rds", final = "data/Les7entites_finies/entities/global_catch_firms_options_raise_false_level0/Rds/georef_dataset_level0_step11global_catch_firms_options_raise_false_level0.rds",   filter_source_authority = c("IATTC")), output_file  = paste0("Markdown/","globalcompglobalwithoutsharkraising_filterIATTC.html"))

 

```


# Analysis of choices on overlaps

For the analysis of the choices on the overlaps we decide to study the impact on the global dataset.

## We already analyze the total treatment of all overlaps

```{r}

fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step5global_catch_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step10global_catch_firms_level0.rds", "step5", "step10")

strates_to_check_doublon <- if ((is.null(params$strates_to_check_doublon))){c("fishingfleet", "gear", "time_start", "time_end", "geographic_identifier", "schooltype", "species", "catchtype", "unit")} else{ params$strates_to_check_doublon}

georef_dataset_level0_step5global_catch_5deg_1m_firms_level0 <- readRDS("~/Documents/Tunaatlas_level1/data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step5global_catch_firms_level0.rds")
strates_to_check_doublon <- c(time_start, unit, species)

pourcent_strates_identiques <- 100*((nrow(georef_dataset_level0_step5global_catch_5deg_1m_firms_level0) - nrow(georef_dataset_level0_step5global_catch_5deg_1m_firms_level0 %>% select(time_start, unit, species) %>% distinct()))/nrow(georef_dataset_level0_step5global_catch_5deg_1m_firms_level0))

```

The choice made on the overlaps is the following. For each combination of `r strates_to_check_doublon` we look at the maximum for each rfmo. 

We notice that for `r pourcent_strates_identiques` of the strata there are no duplicates. The data are therefore `r 100 - pourcent_strates_identiques`% preserved.


## Old method

We take here the example of the total data and for the first step managed by an overlapp previously (step10) (for the moment). Indeed, previously the first 3 overlaps, including all CCSBT, were managed on the basis of the species and not the area. 

### Comparison old method/ new method

#### Lost data keeping only CCSBT for SBF

```{r}

fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step10global_catch_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step10global_catch_firms_level0ancient.rds", "newone", "ancien_keeping_all")

fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step10global_catch_firms_level0.rds",  "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step10global_catch_firms_level0ancient.rds", "newone", "ancien_keeping_allkeepingonlySBF")

rmarkdown::render("comp_sans_shiny.Rmd", params = list(init = "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step10global_catch_firms_level0.rds", final = "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step10global_catch_firms_level0ancient.rds",   filter_species = c("SBF")), output_file  = paste0("Markdown/","step10onSBF"))

```

```{r}

fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step10global_catch_firms_level0ancient.rds", "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step10global_catch_firms_level0reverse.rds", "ancient", "reverse")

```

<!-- ### Comparaison dans l'ancienne méthode : IOTC/WCPFC -->

<!-- ```{r} -->
<!-- #careful has to verify that it is really the init one ctoi and the second one Wcpfc -->

<!-- fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step10global_catch_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step10global_catch_firms_level0ancient.rds", "newone", "ancien_keeping_all") -->
<!-- ``` -->

### Comparaison ORGP/CCSBT

```{r}

```


#### Comparaison IOTC/CCSBT 

```{r}
# fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step9global_catch_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step9global_catch_firms_level0ancient.rds", "iotc_ccbst", "ancien_iotc_ccbst")

rmarkdown::render("comp_sans_shiny.Rmd", params = list(init = "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step9global_catch_firms_level0.rds", final = "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step9global_catch_firms_level0ancient.rds",   filter_species = c("SBF")), output_file  = paste0("Markdown/","iotc_ccsbt_on_sbf"))

```


#### Comparaison ICCAT/CCSBT 

```{r}
# fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step8global_catch_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step8global_catch_firms_level0ancient.rds", "iccat_ccsbt", "ancien_iccat_ccsbt")

rmarkdown::render("comp_sans_shiny.Rmd", params = list(init = "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step8global_catch_firms_level0.rds", final = "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step8global_catch_firms_level0ancient.rds",   filter_species = c("SBF")), output_file  = paste0("Markdown/","iccat_ccsbt_on_sbf"))
```

#### Comparaison WCPFC/CCSBT 

```{r}
# fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step7global_catch_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step7global_catch_firms_level0ancient.rds", "ancien_wcpfc_ccsbt", "ancien_wcpfc_ccsbt")

rmarkdown::render("comp_sans_shiny.Rmd", params = list(init = "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step7global_catch_firms_level0.rds", final = "data/Les7entites_finies/entities/global_catch_firms_level0/Rds/georef_dataset_level0_step7global_catch_firms_level0ancient.rds",   filter_species = c("SBF")), output_file  = paste0("Markdown/","wcpfc_ccsbt_on_sbf"))
```

```{r}
fonction_markdown_si_diff("data/Les7entites_finies/entities/global_catch_5deg_1m_firms_level0/Rds/georef_dataset_level0_step11global_catch_5deg_1m_firms_level0.rds", "data/Les7entites_finies/entities/global_catch_1deg_1m_ps_bb_firms_level0/Rds/georef_dataset_level0_step11global_catch_1deg_1m_ps_bb_firms_level0.rds", "5deg", "1deg")
```



## Analyse du niveau 1

### Analyse de l'ancien niveau 1 sans prise en compte des doublons d'unités

#### Pour les 1 degré 

```{r}
fonction_markdown_si_diff( "data/Les7entites_finies/entities/global_catch_5deg_1m_firms_level0/Rds/georef_dataset_level0_step11global_catch_5deg_1m_firms_level0.rds","data/Les7entites_finies/entities/5deg_level1_reallocate/georef_dataset_step5.rds", "level0_5deg", "level1_5deg")
```

<!-- #### Pour les 5 degrés -->

<!-- ```{r} -->
<!-- fonction_markdown_si_diff("data/Les7entites_finies/entities/5deg_level1_reallocate/georef_dataset_step5.rds", "data/Les7entites_finies/entities/global_catch_5deg_1m_firms_level0/Rds/georef_dataset_level0_step11global_catch_5deg_1m_firms_level0.rds", "level1_5deg", "level0_5deg") -->
<!-- ``` -->



<!-- #### Pour le global  -->

<!-- ```{r} -->

<!-- ``` -->

