---
title: "Data on land and outside competences' area"
author: "Bastien Grasset - IRD"
output:
  html_document:
    toc: true
    theme: united
    number_sections: true
date: '2022-03-14'
params:
  final: "~/Documents/Tunaatlas_level1/jobs/20220622123750/entities/global_catch_1deg_1m_ps_bb_firms_Bastien_filtering_wcpfc_at_the_end_level0/Markdown/treatment_after_binding"
  plotting: "plot"
  world_coastline: "gshhs_world_coastlines"
---

This report presents very shortly the data located on land or outside of the competence area of tRFMOs. It is made for informative purposes for each RFMO as well as for IRD while reviewing the Global Tuna Atlas.

The data presented as "on land" depends on the shape used for continents and oceans.

```{r setup, include=FALSE}
#data/Les7entites_finies/entities/global_catch_5deg_1m_firms_level0/Rds/georef_dataset_level0_step11global_catch_5deg_1m_firms_level0.rds"
#data/Les7entites_finies/entities/5deg_level1_reallocate/georef_dataset_step5.rds"
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(DBI)
library(RPostgres)
library(RPostgreSQL)
library(tmap)
library(dplyr, warn.conflicts = FALSE)
library(sf)
library(tmap)
library(tidyverse)
library(leaflet.minicharts)
library(randomcoloR)
library(RColorBrewer)

```

```{r}

fSpatPlan_Convert2PacificRobinson <- function(df, buff = 0){
  # # Define a long & slim polygon that overlaps the meridian line & set its CRS to match 
  # # that of world
  # 
  # rob_pacific <- "+proj=robin +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
  # longlat <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
  # 
  # polygon <- st_polygon(x = list(rbind(c(-0.0001, 90),
  #                                      c(0, 90),
  #                                      c(0, -90),
  #                                      c(-0.0001, -90),
  #                                      c(-0.0001, 90)))) %>%
  #   st_sfc() %>%
  #   st_set_crs(longlat)
  # 
  # # Modify world dataset to remove overlapping portions with world's polygons
  # df_robinson <- df %>% 
  #   st_difference(polygon) %>% 
  #   st_transform(crs = rob_pacific) # Perform transformation on modified version of world dataset
  # 
  # # notice that there is a line in the middle of Antarctica. This is because we have
  # # split the map after reprojection. We need to fix this:
  # bbox <-  st_bbox(df_robinson)
  # bbox[c(1,3)]  <-  c(-1e-5, 1e-5)
  # polygon_rob <- st_as_sfc(bbox)
  # 
  # crosses <- df_robinson %>%
  #   st_intersects(polygon_rob) %>%
  #   sapply(length) %>%
  #   as.logical %>%
  #   which
  # 
  # # Adding buffer 0
  # df_robinson[crosses,] %>%
  #   st_buffer(buff)
  if(!exists("df_robinson")){
    df_robinson <- df}
  return(df_robinson)
  
}



```

```{r}
data <- readRDS(paste0(as.character(params$final),"/rds.rds"))
# if (!is.null(params$source_authority)) {data <- data%>% dplyr::filter(source_authority == params$source_authority)}

  data <- data%>% dplyr::mutate(unit = case_when(unit %in% c("MT","t","MTNO", "Tons")~ "Tons", unit %in% c("no", "NOMT", "Number of fish", "NO")~"Number of fish"))
cl_cwp_gear_level2 <- read_csv("data/cl_cwp_gear_level2.csv", 
    col_types = cols(Identifier = col_skip(), 
        Abbreviation = col_skip(), Name_Fr = col_skip(), 
        Name_Es = col_skip(), Name_Ar = col_skip()))

data <- data %>% full_join(cl_cwp_gear_level2, by = c("gear" = "Code"))



drv <- dbDriver("PostgreSQL")      
con <- DBI::dbConnect(drv , dbname = "tunaatlas", host = "db-tunaatlas.d4science.org", 
                      port = 5432,
                      user = "tunaatlas_u",
                      password = "21c0551e7ed2911")


query <- "SELECT  code,st_area(geom), geom from area.cwp_grid"
world_sf <- fSpatPlan_Convert2PacificRobinson(st_make_valid(st_read(con, query = query))%>% dplyr::filter(!st_is_empty(.)))

query_area <- paste0("SELECT * FROM area.rfmos_convention_areas_fao")
competence_area <- st_make_valid(st_read(con, query = query_area)) %>% dplyr::filter(!st_is_empty(.))
IOTC_shape <- fSpatPlan_Convert2PacificRobinson(competence_area %>% dplyr::filter(code == "IOTC"))
IATTC_shape <- fSpatPlan_Convert2PacificRobinson(competence_area %>% dplyr::filter(code == "IATTC"))
WCPFC_shape <- fSpatPlan_Convert2PacificRobinson(competence_area %>% dplyr::filter(code == "WCPFC"))
ICCAT_shape <- fSpatPlan_Convert2PacificRobinson(competence_area %>% dplyr::filter(code == "ICCAT"))
query <- "SELECT  code,st_area(geom), geom from area.gshhs_world_coastlines"
continent <- fSpatPlan_Convert2PacificRobinson(st_read(con, query = query)%>% dplyr::filter(!st_is_empty(.)))
query <- "SELECT  code,code_cwp,st_area(geom), geom from area.irregular_areas_task2_iotc"
irregular_iotc <- fSpatPlan_Convert2PacificRobinson(st_read(con, query = query)%>% dplyr::filter(!st_is_empty(.)))
irregular_iotc <-irregular_iotc  %>% dplyr::distinct()
# test <- data %>% dplyr::inner_join(irregular_iotc %>% st_set_geometry(NULL) , by = c("geographic_identifier"= "code")) %>% dplyr::mutate(geographic_identifier = code_cwp)
irregular_iotc[irregular_iotc$code_cwp =="1100030",]$code_cwp <- "9100030"
irregular_iotc[irregular_iotc$code_cwp =="2120060",]$code_cwp <- "8120060"
irregular_iotc[irregular_iotc$code_cwp =="3200050",]$code_cwp <- "7200050"
if(any(irregular_iotc$code_cwp =="4220040")) irregular_iotc[irregular_iotc$code_cwp =="4220040",]$code_cwp <- "8220040"

world_sf <- world_sf %>% dplyr::mutate(code_cwp = code)


tmap_mode("plot")
# tm_shape(st_as_sf(test %>% dplyr::inner_join(world_sf, by = c("geographic_identifier" = "code"))))+tm_polygons()
pakistan <- irregular_iotc %>% dplyr::filter(code_cwp== "3120060")
world_sf_combined <- rbind(pakistan, world_sf)

# world_sf_combined <- gdata::combine(world_sf, irregular_iotc) %>% dplyr::distinct()
# t <- rbind(world_sf_combined[duplicated(world_sf_combined$code_cwp),],world_sf_combined[duplicated(world_sf_combined$code_cwp, fromLast = TRUE),] )

data <- left_join(data, irregular_iotc %>% st_set_geometry(NULL), by =c("geographic_identifier"= "code")) %>% dplyr::mutate(geographic_identifier= ifelse(!is.na(code_cwp), code_cwp, geographic_identifier)) %>% dplyr::select(-c(code_cwp, st_area))

# testtt <- setdiff(irregular_iotc$code_cwp, world_sf$code_cwp)
# 
# test <- t %>% group_by(code, source) %>% slice(1)
# tm_shape(st_as_sf(t))+tm_polygons()+tm_fill(col = "source")
# 
IOTC <- world_sf[IOTC_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(iotc = "iotc")

IATTC <- world_sf[IATTC_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(iattc = "iattc")

WCPFC <- world_sf[WCPFC_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(wcpfc = "wcpfc")

ICCAT <- world_sf[ICCAT_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(iccat = "iccat")



full_join <- full_join(full_join(full_join(full_join(world_sf, IOTC), IATTC), WCPFC), ICCAT) %>% st_set_geometry(NULL) 


full_join[is.na(full_join)] <-  FALSE

full_join <- full_join %>% dplyr::mutate(area_competence = as.factor(gsub("FALSE","",paste0(iotc, iattc, wcpfc, iccat))))
world_sf$continent <- st_within(world_sf, continent) %>% lengths > 0 
world_sf$continent <- str_replace(world_sf$continent, "TRUE","continent")

world_sf <- left_join(world_sf, full_join)

world_sf_with_competence_area <- world_sf %>% dplyr::mutate(area_competence = as.factor(gsub("FALSE","",paste0(iotc, iattc, wcpfc, iccat, continent))))

# world_sf_with_competence_area <- fSpatPlan_Convert2PacificRobinson(world_sf_with_competence_area)


inner_join <- data %>% dplyr::inner_join(world_sf_with_competence_area, by = c("geographic_identifier"="code"))


all_the_data <- inner_join  %>% dplyr::ungroup() %>% group_by(geographic_identifier, st_area, unit, source_authority, area_competence) %>% dplyr::summarise(value= sum(value, na.rm = TRUE))%>% dplyr::distinct() %>% dplyr::inner_join(world_sf%>% dplyr::select(-area_competence) , by = c("geographic_identifier"="code", "st_area") ) %>% dplyr::select(geographic_identifier, st_area, value, geom, unit, source_authority, area_competence)%>% dplyr::mutate(st_area = as.factor(case_when(st_area == 1 ~ "1 deg", st_area == 25 ~ "5 deg", TRUE ~ "> 5 deg")))

mislocated_continent <- all_the_data %>% dplyr::filter(str_detect(area_competence, "continent"))
```

```{r}
en_nombre_continent <- sum((mislocated_continent %>% dplyr::filter(unit == "Number of fish"))$value)
en_tonne_continent <- sum((mislocated_continent %>% dplyr::filter(unit == "Tons") )$value)

```

# Spatial distribution of the mislocated data on land

Those maps represent the value (in tons and in number of fish) of mislocated data for the period 1950-2020.

Is included the name of the RFMO providing data for the square located in lands.

```{r}
if (nrow(mislocated_continent)==0){knitr::knit_exit()}else{
tmap_mode(params$plotting)

tm_shape(st_as_sf(mislocated_continent %>% dplyr::mutate(st_area = as.factor(st_area))))+tm_fill("value")+tm_facets(by=c("st_area","unit"),free.scales = FALSE)+tm_borders()+tm_text("source_authority")#+tm_layout(legend.outside	 =TRUE)#+  tm_shape(continent)+tm_borders() 

}


```

# Characteristics of data located on land

For several parameters, we analyze the distribution of data placed on land, to uncover the features of this type of data.

## RFMO distribution

This graph represents the distribution of the providers of data located on land.

```{r}

mislocated_continent2 <- mislocated_continent %>% group_by(unit, source_authority) %>% arrange(unit,desc(source_authority)) %>% dplyr::summarise(value = sum(value, na.rm = TRUE))  %>% dplyr::ungroup() %>% group_by(unit) %>%  dplyr::mutate(pourcentage = prop.table(value)*100)%>%
    dplyr::mutate(labels = paste0(pourcentage," ",  " % "))%>% arrange(unit,desc( source_authority)) %>% 
  dplyr::mutate(ypos_ligne = cumsum(pourcentage)- 0.5*pourcentage ) %>%
    dplyr::distinct()
ggplot(mislocated_continent2) +aes(
    x = "",
    fill = source_authority,
    colour = source_authority,
    group = source_authority,
    weight = pourcentage
  ) +
  geom_bar(position = "fill") +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  theme_minimal()+ coord_polar("y", start=0)+ geom_text(data = (mislocated_continent2 %>% mutate_if(is.numeric, round)), size = 3,
                           aes( x = 1 ,y = ypos_ligne/100, label = paste0(pourcentage,"%")), color = "black")+
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())+
  labs(x = "", y="") + facet_wrap("unit")

```

As we can see, most of the data located on land is coming from ICCAT and IOTC.

## Temporal distribution

```{r}
mislocated_cwp <- semi_join(data, mislocated_continent, by = "geographic_identifier")
mislocated_continent_time <- mislocated_cwp %>% dplyr::mutate(time_start = lubridate::year(time_start)) %>% group_by(unit, time_start) %>% dplyr::summarise(value = sum(value))
ggplot(mislocated_continent_time ) +
  aes(x = time_start, y = value) +
  geom_col(fill = "#112446") +
  theme_minimal() +
  facet_wrap(vars(unit))+  labs(x = "Year", y = "Value")
```

The data located on land seems to be a punctual issue for the data in fish (with a peak in 2014). However, in tons, the last years seem to be problematic.

## General features

```{r}
library(cowplot)
pie_chart_2 = function(x, data= data,complete = complete) {
  r <- deparse(substitute(x))
  colnames <- enquo(x)
  provisoire_i <-data %>%  group_by(!!colnames#, unit
                                    )  %>% dplyr::summarise(value = sum(value, na.rm = TRUE)) %>% #group_by(unit) %>% 
    arrange(desc(value)) %>%   dplyr::mutate(id = row_number())%>%  
    dplyr::mutate(class = as.factor(ifelse(id<4,!!colnames,"Others"))) %>%
    group_by(class#, unit
             ) %>%  dplyr::summarise(value = sum(value, na.rm = TRUE))%>%dplyr::ungroup()%>% 
    dplyr::select( value, class,#unit
            ) %>%  # group_by(unit) %>% 
      dplyr::mutate(pourcentage = prop.table(value)*100)%>%
    dplyr::mutate(labels = paste0(pourcentage," ",  " % "))%>% arrange(desc(class))%>%
  dplyr::mutate(ypos_ligne = cumsum(pourcentage)- 0.5*pourcentage ) %>%
    dplyr::distinct()
  


  
  provisoire_t <- complete %>%  group_by(!!colnames#, unit
                                        )%>% dplyr::summarise(value = sum(value, na.rm = TRUE)) %>%# group_by(unit) %>%
    arrange(desc(value)) %>%   dplyr::mutate(id = row_number())%>%  
    dplyr::mutate(class = as.factor(ifelse(id<4,!!colnames,"Others"))) %>%
    group_by(class#, unit
             ) %>%  dplyr::summarise(value = sum(value, na.rm = TRUE))%>%dplyr::ungroup()%>% 
    dplyr::select( value, class,#unit
            ) %>%#   group_by(unit) %>% 
    dplyr::mutate(pourcentage = prop.table(value)*100)%>%
    dplyr::mutate(labels = paste0(pourcentage," ",  " % "))%>% arrange(desc(class))%>%
  dplyr::mutate(ypos_ligne = cumsum(pourcentage)- 0.5*pourcentage ) %>%
    dplyr::distinct()
  
set.seed(2) # For reproducibility of random color vector
number <- length(unique(unlist(as.character(c(provisoire_i$class, provisoire_t$class)))))
pal <- brewer.pal(number,"Set1")

  # myColors <- ColorRampPalette(brewer.pal(120,"Spectral"))
# names(myColors) <- levels(dat$grp)
# set.seed(2)
pal = setNames(pal, unique(unlist(as.character(c(provisoire_i$class, provisoire_t$class)))))

ggplot_i <<- ggplot(provisoire_i) +
  aes(
    x = "",
    fill = class,
    group = class,
    weight = pourcentage
  ) +
  geom_bar(position = "fill") +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  theme_minimal()+ coord_polar("y", start=0)+ geom_text(data = (provisoire_i %>% mutate_if(is.numeric, round)), size = 3,
                           aes( x = 1 ,y = ypos_ligne/100, label = paste0(pourcentage,"%")), color = "black")+
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())+
  labs(x = "", y="")+ scale_fill_manual(values=pal)+ guides(fill=guide_legend(title=toupper(r)))
legend <- cowplot::get_legend(ggplot_i)

ggplot_t <<- ggplot(provisoire_t) +
  aes(
    x = "",
    fill = class,
     group = class,
    weight = pourcentage
  ) +
  geom_bar(position = "fill") +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  theme_minimal()+ coord_polar("y", start=0)+ geom_text(data = (provisoire_t %>% mutate_if(is.numeric, round)), size = 3,
                           aes( x = 1, y = ypos_ligne/100, label = paste0(pourcentage,"%")), color = "black")+
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())+
  labs(x = "", y="")+ scale_fill_manual(values=pal)+ theme(legend.position = "none")

title <- ggdraw() + 
  draw_label(
    paste0("Distribution in value for the dimension : ",r),
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )
graph <<- plot_grid(ggplot_i+ theme(legend.position = "none"), ggplot_t,nrow = 2,labels = c( paste0(titre_dataset),paste0( "Complete")),
  label_size = 10)

plot_grid(title, nrow=2,plot_grid(graph,legend,ncol = 2),
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1))+
    theme(plot.background = element_rect(color = "black"))


}
titre_dataset <- "Located on land"
# pie_chart_2(fishingfleet, mislocated_cwp, data)
# 
# plot_grid(graph,title)

```

### Fishingfleet in tons

```{r}

pie_chart_2(fishingfleet, mislocated_cwp %>% dplyr::filter(unit == "Tons"), data%>% dplyr::filter(unit == "Tons"))

```

Spain, Irland and Belize, represents a higher proportion of value on land than the value in Ocean.

### Fishingfleet in numbers

```{r}
pie_chart_2(fishingfleet, mislocated_cwp %>% dplyr::filter(unit == "Number of fish"), data%>% dplyr::filter(unit == "Number of fish"))
```

In number, Seychelles Brasil and USA are locating more on land relatively compared to what they declare in Oceans.

### Species in tons

```{r}
pie_chart_2(species, mislocated_cwp %>% dplyr::filter(unit == "Tons"), data%>% dplyr::filter(unit == "Tons"))
```

Yellowfin tuna is not located on land at all. Albacore, Patudo, and other fishes are more located on land compared to the number of catches in tons. Skipjack still represents the majority of captures in tons declared on land, however, it represents also half of the catches declared.

```{r}
all_the_data3 <- all_the_data %>% dplyr::mutate(continent = ifelse(area_competence != "continent", "ocean", "continent"))

```

```{r}
# st_geometry(all_the_data3) <- NULL
final <- all_the_data3 %>% group_by(continent, unit) %>% dplyr::summarise(value = sum(value))
# all_the_data2_without_continent <- all_the_data %>% dplyr::filter(area_competence != "continent")
# value_without_continent <- sum(all_the_data2_without_continent$value, na.rm =TRUE)

en_nombre_continent <- pull(final %>% dplyr::filter(unit == "Number of fish") %>% dplyr::filter(continent == "continent"))
en_nombre_ocean <- pull(final %>% dplyr::filter(unit == "Number of fish") %>% dplyr::filter(continent == "ocean"))
en_tonne_continent <- pull(final %>% dplyr::filter(unit == "Tons") %>% dplyr::filter(continent == "continent"))
en_tonne_ocean <- pull(final %>% dplyr::filter(unit == "Tons") %>% dplyr::filter(continent == "ocean"))

perte_en_nombre <- (en_nombre_continent / (en_nombre_ocean+en_nombre_continent))*100
perte_en_tonne <- (en_tonne_continent/ (en_tonne_continent+en_tonne_ocean))*100

# value_with_continent <- sum(all_the_data$value, na.rm = TRUE)

# perte_en_pourcent_conitnent <- ((value_with_continent-value_without_continent)/value_with_continent)*100
```

The data placed on land represents (at the beginning of treatments in the GTA), `r perte_en_nombre` % in number and `r perte_en_tonne` % in tons.

# Data located outside the competence area of the tRFMOs

Some of the data is correctly placed in oceans, however it is placed by RFMO in area which does not correspond to the competence zone of the source authority.

```{r}

# mislocated <- inner_join %>%dplyr::filter(!str_detect(area_competence, "continent")) %>%  dplyr::ungroup() %>% dplyr::select(area_competence, source_authority, value, unit, geom) %>% dplyr::mutate(area_competence = toupper(area_competence)) %>%  dplyr::mutate(mislocated = case_when(source_authority =="CCSBT" ~TRUE, area_competence%in%c("IATTC", "ICCAT", "IOTC", "WCPFC") & area_competence == source_authority ~ TRUE,
#                               area_competence == "IOTCWCPFC" & source_authority %in% c("IOTC", "WCPFC")  ~ TRUE,
#                               area_competence == "IATTCWCPFC" & source_authority %in% c("IATTC", "WCPFC")  ~ TRUE, tolower(area_competence) == area_competence ~ TRUE, 
#                               TRUE ~ FALSE))

mislocated <- inner_join %>% dplyr::mutate(area_competence = as.character(area_competence)) %>% dplyr::filter(!str_detect(inner_join$area_competence, "continent")) %>% dplyr::filter(!is.null(area_competence))%>% dplyr::filter(area_competence != "")%>% dplyr::mutate(area_competence= as.factor(area_competence)) %>%  dplyr::ungroup() %>% dplyr::select(area_competence, source_authority, value, unit, geom) %>% dplyr::mutate(source_authority = tolower(source_authority)) %>%  dplyr::mutate(mislocated = case_when(str_detect(area_competence, source_authority) == TRUE ~ TRUE, area_competence == source_authority ~ TRUE, source_authority == "CCSBT"~TRUE,
                              TRUE ~ FALSE))

final <- mislocated %>% group_by(mislocated, unit) %>% dplyr::summarise(value = sum(value))
en_nombre_false<- pull(final %>% dplyr::filter(unit == "Number of fish") %>% dplyr::filter(mislocated == FALSE))
en_nombre_true <- pull(final %>% dplyr::filter(unit == "Number of fish") %>% dplyr::filter(mislocated == TRUE))
en_tonne_false <- pull(final %>% dplyr::filter(unit == "Tons") %>% dplyr::filter(mislocated == FALSE))
en_tonne_true <- pull(final %>% dplyr::filter(unit == "Tons") %>% dplyr::filter(mislocated == TRUE))

perte_en_nombre2 <- (en_nombre_false / (en_nombre_true+en_nombre_false))*100
perte_en_tonne2 <- (en_tonne_false/ (en_tonne_false+en_tonne_true))*100


```

```{r eval=FALSE}
# tm_shape(IOTC)+tm_fill(alpha = 0.2, col = "red")+tm_shape(IATTC)+tm_fill(alpha = 0.2, col = "yellow")+tm_shape(ICCAT)+tm_fill(alpha = 0.2, col = "purple")+tm_shape(WCPFC)+tm_fill(alpha = 0.2, col = "skyblue")+tm_shape(st_as_sf(mislocated %>% dplyr::filter(mislocated ==FALSE) %>% dplyr::filter(source_authority!="CCSBT")))+tm_polygons(col = "source_authority")+tm_facets("unit")
```

```{r}
fonction_outside_com_zone = function(x){
tm_shape((WCPFC_shape %>% dplyr::mutate(name = "WCPFC")))+tm_borders(col ="red")+tm_text("name")+tm_shape((ICCAT_shape%>% dplyr::mutate(name = "ICCAT")))+tm_borders( col = "yellow")+tm_text("name")+tm_shape((IOTC_shape%>% dplyr::mutate(name = "IOTC")))+tm_borders( col = "purple")+tm_text("name")+tm_shape((IATTC_shape%>% dplyr::mutate(name = "IATTC")))+tm_borders( col = "skyblue")+tm_text("name")+tm_shape((st_as_sf(mislocated) %>% dplyr::filter(mislocated ==FALSE) %>% dplyr::filter(source_authority!="ccsbt") %>%  dplyr::filter(area_competence != "") %>% dplyr::filter(!is.null(area_competence))%>% dplyr::filter(unit == x))) +tm_polygons(col = "source_authority")+tm_text("source_authority")
  }
```

## Data outside competences' area in tons

```{r}
tmap_mode("plot")
fonction_outside_com_zone("Tons")
```

## Data outside competences' area in number of fish

```{r}
fonction_outside_com_zone("Number of fish")
```

As we can see, some of those areas correspond to cwp squares at the border of the competence zone. However, some of the data of the IATTC and ICCAT are placed far from the competence zone.

How the data outside the competence zone should be handled?

For now, they are not handled in any way.
