---
title: "Data with potential mistakes"
always_allow_html: true
output:
  bookdown::pdf_document2:
    toc: !expr if(!exists('child')) {TRUE} else {child}
    number_sections: TRUE
    keep_tex: true
    extra_dependencies: ["adjustbox", "subfig"]
  bookdown::html_document2:
    toc: !expr if(!exists('child')) {TRUE} else {child}
    number_sections: TRUE
    date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  final: "~/Documents/Tunaatlas_level1/jobs/20220927110301_global_catch/entities/global_catch_1deg_level1_final/Markdown/Modifying_IOTC_cwp_errors"
  rawdata: "data/rawdata"
  dbname: "tunaatlas_sandbox2"
  host: "localhost"
  port: 5432
  user: "tunaatlas_u"
  password: ""
  plotting: "plot"
  fact: "catch"
  world_coastline: "gshhs_world_coastlines"
  con: con
  filtering: !r list(species = NULL)


---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)


```


```{r include=FALSE}

if(!(require(base))){ 
  install.packages("base") 
  (require(base))} 
if(!(require(flextable))){ 
  install.packages("flextable") 
  (require(flextable))} 

if(!(require(ggplot2))){ 
  install.packages("ggplot2") 
  (require(ggplot2))} 
if(!(require(dplyr))){ 
  install.packages("dplyr") 
  (require(dplyr))} 
if(!(require(RColorBrewer))){ 
  install.packages("RColorBrewer") 
  (require(RColorBrewer))} 
if(!(require(stats))){ 
  install.packages("stats") 
  (require(stats))} 
if(!(require(cowplot))){ 
  install.packages("cowplot") 
  (require(cowplot))} 
if(!(require(readr))){ 
  install.packages("readr") 
  (require(readr))} 
if(!(require(RPostgres))){ 
  install.packages("RPostgres") 
  (require(RPostgres))} 
if(!(require(RPostgreSQL))){ 
  install.packages("RPostgreSQL") 
  (require(RPostgreSQL))} 
if(!(require(sf))){ 
  install.packages("sf") 
  (require(sf))} 
if(!(require(tmap))){ 
  install.packages("tmap") 
  (require(tmap))} 
if(!(require(stringr))){ 
  install.packages("stringr") 
  (require(stringr))} 
if(!(require(lubridate))){ 
  install.packages("lubridate") 
  (require(lubridate))} 
if(!require(sutdycatchesird)){
  if(!require(remotes)){
    install.packages("remotes")
  }
  require(remotes)
  install_github("BastienIRD/sutdycatchesird")
  require(sutdycatchesird)
}
if(!(require(utils))){ 
  install.packages("utils") 
  (require(utils))} 
if(!(require(DBI))){ 
  install.packages("DBI") 
  (require(DBI))} 

if(require("htmltools"))
  set_flextable_defaults(
    font.size = 30,
    font.color = "black",
    table.layout = "fixed",
    digits = NULL,
    theme_fun = "theme_box"
  )
div(flextable_html_dependency())



```

# How much data is mislocated on continents ?

```{r}
conn <- params$con


query <- "SELECT code, st_area(geom), geom from area.cwp_grid"
out <- try((world_sf <- st_read(conn, query = query)), silent = TRUE)
if(!any(class(out) == "error")){conn <- DBI::dbConnect(RPostgres::Postgres() , dbname = params$dbname, host = params$host,   port = params$port,
                                                       user = params$user,
                                                       password = params$password)}

data <- readRDS(paste0(as.character(params$final),"/rds.rds"))
data <- data%>% dplyr::mutate(unit = case_when(unit %in% c("MT","t","MTNO", "Tons")~ "Tons", unit %in% c("no", "NOMT", "Number of fish", "NO")~"Number of fish"))
cl_cwp_gear_level2 <- read_csv(file.path("data","cl_cwp_gear_level2.csv"), 
                               col_types = cols(Identifier = col_skip(), 
                                                Abbreviation = col_skip(), Name_Fr = col_skip(), 
                                                Name_Es = col_skip(), Name_Ar = col_skip()))

data <- data %>% dplyr::full_join(cl_cwp_gear_level2, by = c("gear" = "Code"))



query <- "SELECT  code,st_area(geom), geom from area.cwp_grid"
world_sf <- st_make_valid(st_read(conn, query = query))%>% dplyr::filter(!st_is_empty(.))

query_area <- paste0("SELECT * FROM area.rfmos_convention_areas_fao")
competence_area <- st_make_valid(st_read(conn, query = query_area)) %>% dplyr::filter(!st_is_empty(.))
IOTC_shape <- sf::st_make_valid(competence_area %>% dplyr::filter(code == "IOTC"))
IATTC_shape <- sf::st_make_valid(competence_area %>% dplyr::filter(code == "IATTC"))
WCPFC_shape <- sf::st_make_valid(competence_area %>% dplyr::filter(code == "WCPFC"))
ICCAT_shape <- sf::st_make_valid(competence_area %>% dplyr::filter(code == "ICCAT"))
query <- "SELECT  code,st_area(geom), geom from area.gshhs_world_coastlines"
continent <- sf::st_read(conn, query = query)%>% dplyr::filter(!st_is_empty(.))
query <- "SELECT  code,code_cwp,st_area(geom), geom from area.irregular_areas_task2_iotc"
irregular_iotc <- sf::st_read(conn, query = query)%>% dplyr::filter(!st_is_empty(.))
irregular_iotc <-irregular_iotc  %>% dplyr::distinct()

irregular_iotc[irregular_iotc$code_cwp =="1100030",]$code_cwp <- "9100030"
irregular_iotc[irregular_iotc$code_cwp =="2120060",]$code_cwp <- "8120060"
irregular_iotc[irregular_iotc$code_cwp =="3200050",]$code_cwp <- "7200050"
if(any(irregular_iotc$code_cwp =="4220040")) irregular_iotc[irregular_iotc$code_cwp =="4220040",]$code_cwp <- "8220040"

world_sf <- sf::st_make_valid(world_sf %>% dplyr::mutate(code_cwp = code))
world_sf <- world_sf[sf::st_is_valid(world_sf),]

pakistan <- irregular_iotc %>% dplyr::filter(code_cwp== "3120060")
world_sf_combined <- rbind(pakistan, world_sf)


data <- dplyr::left_join(data, irregular_iotc %>% st_set_geometry(NULL), by =c("geographic_identifier"= "code")) %>% dplyr::mutate(geographic_identifier= ifelse(!is.na(code_cwp), code_cwp, geographic_identifier)) %>% dplyr::select(-c(code_cwp, st_area))



IOTC <- world_sf[IOTC_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(iotc = "iotc")

IATTC <- world_sf[IATTC_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(iattc = "iattc")

WCPFC <- world_sf[WCPFC_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(wcpfc = "wcpfc")

ICCAT <- world_sf[ICCAT_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(iccat = "iccat")



full_join <- dplyr::full_join(dplyr::full_join(dplyr::full_join(dplyr::full_join(world_sf, IOTC), IATTC), WCPFC), ICCAT) %>% st_set_geometry(NULL) 


full_join[is.na(full_join)] <-  FALSE

full_join <- full_join %>% dplyr::mutate(area_competence = as.factor(gsub("FALSE","",paste0(iotc, iattc, wcpfc, iccat))))
world_sf$continent <- st_within(world_sf, continent) %>% lengths > 0 
world_sf$continent <- str_replace(world_sf$continent, "TRUE","continent")

world_sf <- dplyr::left_join(world_sf, full_join)

world_sf_with_competence_area <- world_sf %>% dplyr::mutate(area_competence = as.factor(gsub("FALSE","",paste0(iotc, iattc, wcpfc, iccat, continent))))


inner_join <- data %>% dplyr::inner_join(world_sf_with_competence_area, by = c("geographic_identifier"="code"))
query2 <- "SELECT  code,st_area(geom), geom from area.cwp_grid"
world_sf2 <- st_make_valid(st_read(conn, query = query2))%>% dplyr::filter(!st_is_empty(.))%>%dplyr::rename(geographic_identifier=code)

all_the_data <- inner_join  %>% ungroup() %>% dplyr::group_by(geographic_identifier, st_area, unit, source_authority, area_competence) %>% dplyr::summarise(value= sum(value, na.rm = TRUE))%>% dplyr::distinct() %>% dplyr::inner_join(world_sf2 , by = c("geographic_identifier", "st_area") ) 


all_the_data <- all_the_data %>% dplyr::select(geographic_identifier, st_area, value, geom, unit, source_authority,area_competence)


mislocated_continent <- all_the_data %>% dplyr::filter(str_detect(area_competence, "continent"))

if (nrow(mislocated_continent)==0){knitr::knit_exit()}else{
  
  
  image <- tm_shape(st_as_sf(mislocated_continent %>% dplyr::mutate(st_area = as.factor(st_area))))+tm_fill("value")+tm_facets(by=c("st_area","unit"))+tm_shape(continent)+tm_borders()#+tm_text("source_authority")#+tm_shape(continent)+tm_borders() 
  
  
  image2 <- tm_shape(st_as_sf(mislocated_continent %>% dplyr::mutate(st_area = as.factor(st_area))))+tm_fill("source_authority")+tm_facets(by=c("st_area","unit"))+tm_shape(continent)+tm_borders()
}
FitFlextableToPage <- function(ft, pgwidth = 6){
  
  ft_out <- ft %>% autofit()
  
  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}
kable2 =function(x){as_image(kable(x))}
qflextable2 =function(x, captionn = NULL, autonumm = autonum, pgwidth = 6, colour = FALSE){
 y<-x
 y <- y %>% dplyr::mutate_if(is.factor, as.character) %>% dplyr::mutate_if(is.character, ~str_replace_all( ., ",", ", \n" )) %>% 
  dplyr::mutate_if(is.character,~str_replace_all( ., "_", "-" )) %>% dplyr::mutate_if(is.numeric, function(.){round(.,2)})
  flextable <- flextable(y)
  if(colour){
  flextable <- flextable %>% 
          color(~ `Difference (in % of tons)` < 0, color = "green",~ `Difference (in % of tons)`) %>% 
          color(~ `Difference (in % of tons)` >0, color = "red",~ `Difference (in % of tons)`)%>%   color(~ `Difference (in % of fish)` < 0, color = "green",~ `Difference (in % of fish)`) %>% 
          color(~ `Difference (in % of fish)` >0, color = "red",~ `Difference (in % of fish)`)%>%color(~ `Difference (in % of lines)` < 0, color = "green",~ `Difference (in % of lines)`) %>% 
          color(~ `Difference (in % of lines)` >0, color = "red",~ `Difference (in % of lines)`)
  } 
  if(!is.null(captionn)){flextable_captionned <- set_caption(flextable, caption = captionn,  style = "Table Caption")} else {flextable_captionned <- flextable}
  ft_out <- flextable_captionned %>% autofit()
  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))

  return(ft_out)

}

```

```{r}

qflextable2(mislocated_continent %>%  group_by(unit) %>% summarise(value = sum(value)), captionn = "Value of data reported on continent by unit ")
```

Those next maps will presents where and by who the mislocated data is reported.


# Distribution of mislocated data 


```{r}

image <- tm_shape(st_as_sf(mislocated_continent %>% dplyr::mutate(st_area = as.factor(st_area))))+tm_fill("value")+tm_facets(by=c("st_area","unit"))+tm_shape(continent)+tm_borders()#+tm_text("source_authority")#+tm_shape(continent)+tm_borders() 


image2 <- tm_shape(st_as_sf(mislocated_continent %>% dplyr::mutate(st_area = as.factor(st_area))))+tm_fill("source_authority")+tm_facets(by=c("st_area","unit"))+tm_shape(continent)+tm_borders()

map_unit <- list(list(image, image2))



```


```{r eval=TRUE}
map_unit_knit = function(map){
  assign("map_for_knit_where", map[1][[1]], envir = environment())
  assign("map_for_knit_who", map[2][[1]], envir = environment())
  knitr::knit_child(text = c(
    '',
    '',
    '```{r echo = FALSE, fig.cap = paste0("Distribution of mislocated data in value")}',
    '',
    'map_for_knit_where',
    '```',
    '',
    '```{r echo = FALSE, fig.cap = paste0("Contributor of mislocated data")}',
    '',
    'map_for_knit_who',
    '```',
    '',
    
    ''
  ), envir = environment(), quiet= TRUE)
}
```


```{r results='asis'}
try(map_unit_knit_list <- lapply(map_unit, FUN = map_unit_knit ))
```

```{r results='asis'}
cat(unlist(map_unit_knit_list), sep = "\n")
```


```{r}
pie_chart_2_default <- studycatchesird::pie_chart_2

function_pie_chart_df <- function(dimension, ...){
  formals(pie_chart_2_default)$dimension <- dimension
  dimension_returned <- dimension
  pie_chart = pie_chart_2_default(...)
  if(exists("pie_chart$df")){
    df = pie_chart$df
    pie_chart = pie_chart$plot} else{
      pie_chart = pie_chart
      df = NULL}
  
  if(!is.null(df)){
    df <- qflextable2(df, captionn = paste0("Strata movement for the dimension : ", dimension_returned))}
  return(list(pie_chart=pie_chart,df=df, dimension=dimension_returned))
}

# resume_knit_child = function(x){
#   
#   knitr::knit_child(text = c(
#     '',
#     '```{r}', 
#     'dimension_title <- gsub("_","..",x$dimension)',
#     '',
#     '```',
#     '',
#     '',
#     '',
#     '```{r echo = FALSE ,fig.cap = paste0("Distribution in value for the dimension : ",(dimension_title))}',
#     '',
#     'x$pie_chart',
#     '```',
#     '',
#     '',
#     '',
#     '```{r results = "asis", eval= !is.null(x$df)}',
#     'x$df',
#     '',
#     '',
#     '```',
#     '',
#     '', 
#     ''
#     
#     
#     
#     
#   ), envir = environment(), quiet= TRUE)
# }
list_pie_chart <- list("fishingfleet","source_authority")

pie_charts_multiple <- lapply(list_pie_chart,FUN = function_pie_chart_df, first= mislocated_continent %>% ungroup() %>% select(geographic_identifier) %>% inner_join(data, by = "geographic_identifier"), topn = 3, title_yes_no = FALSE, titre_1 = "Mislocated data" )

figures<- lapply(pie_charts_multiple, function(x){x$pie_chart})

dimension_title_subfigures <- lapply(pie_charts_multiple, function(x){paste0("Distribution in value for the dimension ", x$dimension)})





```

```{r echo=FALSE, fig.cap='Repartition of the mislocated data for several dimensions', fig.subcap=c(unlist(gsub("_","..",dimension_title_subfigures))), fig.ncol = 2, out.width = "50%", fig.align = "center"}

for (i in figures){plot(i)}

```

```{r eval=FALSE}

mislocated_continent2 <- mislocated_continent %>% dplyr::group_by(unit, source_authority) %>% arrange(unit,desc(source_authority)) %>% dplyr::summarise(value = sum(value, na.rm = TRUE))  %>% ungroup() %>% dplyr::group_by(unit) %>%  dplyr::mutate(pourcentage = prop.table(value)*100)%>%
  dplyr::mutate(labels = paste0(pourcentage," ",  " % "))%>% arrange(unit,desc( source_authority)) %>% 
  dplyr::mutate(ypos_ligne = cumsum(pourcentage)- 0.5*pourcentage ) %>%
  dplyr::distinct()
ggplot(mislocated_continent2) +aes(
  x = "",
  fill = source_authority,
  colour = source_authority,
  group = source_authority,
  weight = pourcentage
) +
  geom_bar(position = "fill") +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  theme_minimal()+ coord_polar("y", start=0)+ geom_text(data = (mislocated_continent2 %>% mutate_if(is.numeric, round)), size = 3,
                                                        aes( x = 1 ,y = ypos_ligne/100, label = paste0(pourcentage,"%")), color = "black")+
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())+
  labs(x = "", y="") + facet_wrap("unit")

```

```{r}
all_the_data3 <- all_the_data %>% dplyr::mutate(continent = ifelse(area_competence != "continent", "ocean", "continent"))

```


```{r}
final <- all_the_data3 %>% dplyr::group_by(continent, unit) %>% dplyr::summarise(value = sum(value))


en_nombre_continent <- pull(final %>% dplyr::filter(unit == "Number of fish") %>% dplyr::filter(continent == "continent"))
en_nombre_ocean <- pull(final %>% dplyr::filter(unit == "Number of fish") %>% dplyr::filter(continent == "ocean"))
en_tonne_continent <- pull(final %>% dplyr::filter(unit == "Tons") %>% dplyr::filter(continent == "continent"))
en_tonne_ocean <- pull(final %>% dplyr::filter(unit == "Tons") %>% dplyr::filter(continent == "ocean"))

perte_en_nombre <- (en_nombre_continent / (en_nombre_ocean+en_nombre_continent))*100
perte_en_tonne <- (en_tonne_continent/ (en_tonne_continent+en_tonne_ocean))*100


```

Removing the data placed on the continents, the losses at the end of level 0 amount to `r perte_en_nombre` % in number and `r perte_en_tonne` % in tons. 

We are now interested in the mislocated data

```{r}


mislocated <- inner_join %>% dplyr::mutate(area_competence = as.character(area_competence)) %>% dplyr::filter(!str_detect(inner_join$area_competence, "continent")) %>% dplyr::filter(!is.null(area_competence))%>% dplyr::filter(area_competence != "")%>% dplyr::mutate(area_competence= as.factor(area_competence)) %>%  ungroup() %>% dplyr::select(area_competence, source_authority, value, unit, geom) %>% dplyr::mutate(source_authority = tolower(source_authority)) %>%  dplyr::mutate(mislocated = case_when(str_detect(area_competence, source_authority) == TRUE ~ TRUE, area_competence == source_authority ~ TRUE, source_authority == "CCSBT"~TRUE,
                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        TRUE ~ FALSE))

final <- mislocated %>% dplyr::group_by(mislocated, unit) %>% dplyr::summarise(value = sum(value))
en_nombre_false<- pull(final %>% dplyr::filter(unit == "Number of fish") %>% dplyr::filter(mislocated == FALSE))
en_nombre_true <- pull(final %>% dplyr::filter(unit == "Number of fish") %>% dplyr::filter(mislocated == TRUE))
en_tonne_false <- pull(final %>% dplyr::filter(unit == "Tons") %>% dplyr::filter(mislocated == FALSE))
en_tonne_true <- pull(final %>% dplyr::filter(unit == "Tons") %>% dplyr::filter(mislocated == TRUE))

perte_en_nombre <- (en_nombre_false / (en_nombre_true+en_nombre_false))*100
perte_en_tonne <- (en_tonne_false/ (en_tonne_false+en_tonne_true))*100


```

```{r}

```


```{r}
image <- tm_shape(WCPFC_shape %>% dplyr::mutate(name = "WCPFC"))+tm_borders( col = "red")+tm_text("name")+tm_shape(ICCAT_shape%>% dplyr::mutate(name = "ICCAT"))+tm_borders( col = "yellow")+tm_text("name")+tm_shape(IOTC_shape%>% dplyr::mutate(name = "IOTC"))+tm_borders( col = "purple")+tm_text("name")+tm_shape(IATTC_shape%>% dplyr::mutate(name = "IATTC"))+tm_borders( col = "skyblue")+tm_text("name")+tm_shape(st_as_sf(mislocated %>% dplyr::filter(mislocated ==FALSE) %>% dplyr::filter(source_authority!="ccsbt") %>%  dplyr::filter(area_competence != "") %>% dplyr::filter(!is.null(area_competence))))+tm_polygons(col = "source_authority")+tm_facets("unit") +tm_shape(continent)+tm_borders()
image
```


Removing data placed on continents, as well as data from an rfmo in an area outside their jurisdiction, the losses at the end of level 0 amount to `r perte_en_nombre` % in number and `r perte_en_tonne` % in tons. 

```{r}
rawdata<- readRDS(paste0(params$rawdata,".rds")) #%>% dplyr::filter(source_authority == params$source_authority)
rdslevel0 <- rawdata

strata_nomt <- rdslevel0 %>% dplyr::filter(unit %in% c("NOMT")) #%>% dplyr::select(-c(schooltype, catchtype, fishingfleet)) %>% group_by_all() %>% dplyr::summarise(value = sum(value)) #%>% dplyr::mutate(unit = "NO", unit_target = "MT")
# strata_no <- rdslevel0 %>% dplyr::filter(unit == "NO") %>% dplyr::mutate(source= "strata_no")
# strata_nomt_2 <- strata_nomt %>% dplyr::mutate(source = "strata_nomt")
# t <- gdata::combine(strata_no, strata_nomt)
# r <- dplyr::full_join(strata_no, strata_nomt_2, by = c("fishingfleet", "gear", "time_start", "time_end", "geographic_identifier",
# "schooltype", "species", "catchtype", "unit", "source_authority")) %>% dplyr::filter(!is.na(source.x) & !is.na(source.y))
# upp is to check if data in no could be converted

strata_mtno <- rdslevel0 %>% dplyr::filter(unit %in% c("MTNO")) #%>% dplyr::select(-c(schooltype, catchtype ,fishingfleet)) %>% group_by_all() %>% dplyr::summarise(value=sum(value))#%>% dplyr::mutate(unit = "MT", unit_target = "NO")

strata_converted_level0 <-  rbind(strata_nomt, strata_mtno) %>% ungroup() %>% dplyr::select(-c(value)) %>% dplyr::distinct()

conversion_factor_level0 <- rbind(dplyr::inner_join(strata_nomt , strata_mtno, by = setdiff(colnames(strata_mtno), c("value", "unit") )) %>% dplyr::rename(NO =value.x, MT = value.y) %>%
                                    dplyr::group_by(gear, time_start, time_end, geographic_identifier, species, source_authority, schooltype, catchtype ,fishingfleet) %>% 
                                    dplyr::summarise(NO = sum(NO), MT = sum(MT)) %>% ungroup()#%>% dplyr::select(-c(unit.y, unit.x))
                                  , dplyr::inner_join(strata_mtno , strata_nomt, by = setdiff(colnames(strata_mtno), c("value", "unit") )) %>% dplyr::rename(MT =value.x, NO = value.y)%>%
                                    dplyr::group_by(gear, time_start, time_end, geographic_identifier, species, source_authority, schooltype, catchtype ,fishingfleet)%>%
                                    dplyr::summarise(NO = sum(NO), MT = sum(MT)) %>%ungroup() #%>%  dplyr::select(-c(unit.y, unit.x))
)%>% dplyr::distinct()%>%
  dplyr::group_by(gear, time_start, time_end, geographic_identifier, species, source_authority, schooltype, catchtype ,fishingfleet) %>%
  dplyr::summarise(NO = sum(NO), MT = sum(MT)) %>% dplyr::mutate(conversion_factor = MT/NO) %>% dplyr::distinct()
```

```{r}
knitr::knit_exit()
```


# Absurd conversion factors

We analyse here the data with conversion factors "absurd", meaning being superior to the maximum catch reported for the fish of this species.

We compare the data of this conversion factors absurd, with the total data to see any pattern.

```{r}
`%notin%` <- Negate(`%in%`)
max_conversion_factor <- read_csv("data/max_conversion_factor.csv", 
    col_types = cols(max_weight = col_double(), 
        min_weight = col_double()))
View(max_conversion_factor)
absurd_conversion_factor <- inner_join(conversion_factor_level0, max_conversion_factor, by= c("species"))
# absurd_conversion_factor <- conversion_factor_level0 %>% dplyr::filter((conversion_factor>0.05 & species == "SKJ") | (conversion_factor > 0.09 & species == "ALB") |(conversion_factor>0.2 & species == "YFT") | (conversion_factor >0.5 & species =="SWO")| (conversion_factor>0.2 &species == "BET") | (species %notin% c("ALB","SKJ","SWO", "YFT", "BET")))
```

```{r}
titre_1 <- "Strange conversion factors"
absurd_conversion_factor_tons <- absurd_conversion_factor  %>%  dplyr::rename(value=MT) %>% dplyr::mutate(unit="MT")
strange <- studycatchesird::pie_chart_2(fishingfleet,first=absurd_conversion_factor_tons,second=rawdata )
```


```{r echo=FALSE,  fig.cap='Repartition of fishingfleet for impossible conversion factors'}
strange
```


```{r}
# titre_1 <- "Original data"
# original <- studycatchesird::pie_chart_2(fishingfleet, mapped_data %>% dplyr::filter(unit %in% c("Tons","MT","MTNO")))
# original
# plot_grid(strange, original)
```

We can see that the repartition of the value in tons is very different in the data where the conversion factor seems too big. 

# Mislocated data

```{r}

rawdata <- readRDS("data/rawdata.rds")
data <- rawdata%>% dplyr::mutate(unit = case_when(unit %in% c("MT","t","MTNO", "Tons")~ "Tons", unit %in% c("no", "NOMT", "Number of fish", "NO")~"Number of fish"))
cl_cwp_gear_level2 <- read_csv("data/cl_cwp_gear_level2.csv", 
                               col_types = cols(Identifier = col_skip(), 
                                                Abbreviation = col_skip(), Name_Fr = col_skip(), 
                                                Name_Es = col_skip(), Name_Ar = col_skip()))

data <- data %>% dplyr::full_join(cl_cwp_gear_level2, by = c("gear" = "Code"))


query <- "SELECT  code,st_area(geom), geom from area.cwp_grid"

world_sf <- st_make_valid(st_read(conn, query = query))%>% dplyr::filter(!st_is_empty(.))

query_area <- paste0("SELECT * FROM area.rfmos_convention_areas_fao")
competence_area <- st_make_valid(st_read(conn, query = query_area)) %>% dplyr::filter(!st_is_empty(.))
IOTC_shape <- competence_area %>% dplyr::filter(code == "IOTC")
IATTC_shape <- competence_area %>% dplyr::filter(code == "IATTC")
WCPFC_shape <- competence_area %>% dplyr::filter(code == "WCPFC")
ICCAT_shape <- competence_area %>% dplyr::filter(code == "ICCAT")
query <- "SELECT  code,st_area(geom), geom from area.gshhs_world_coastlines"
continent <- st_read(conn, query = query)%>% dplyr::filter(!st_is_empty(.))
query <- "SELECT  code,code_cwp,st_area(geom), geom from area.irregular_areas_task2_iotc"
irregular_iotc <- st_read(conn, query = query)%>% dplyr::filter(!st_is_empty(.))
irregular_iotc <-irregular_iotc  %>% dplyr::distinct()

world_sf <- sf::st_make_valid(world_sf %>% dplyr::mutate(code_cwp = code))
world_sf <- world_sf[sf::st_is_valid(world_sf),]

# tm_shape(st_as_sf(test %>% dplyr::inner_join(world_sf, by = c("geographic_identifier" = "code"))))+tm_polygons()
pakistan <- irregular_iotc %>% dplyr::filter(code_cwp== "3120060")
world_sf_combined <- rbind(pakistan, world_sf)
# world_sf_combined <- gdata::combine(world_sf, irregular_iotc) %>% dplyr::distinct()
# t <- rbind(world_sf_combined[duplicated(world_sf_combined$code_cwp),],world_sf_combined[duplicated(world_sf_combined$code_cwp, fromLast = TRUE),] )

data <- dplyr::left_join(data, irregular_iotc %>% st_set_geometry(NULL), by =c("geographic_identifier"= "code")) %>% dplyr::mutate(geographic_identifier= ifelse(!is.na(code_cwp), code_cwp, geographic_identifier)) %>% dplyr::select(-c(code_cwp, st_area))

# testtt <- setdiff(irregular_iotc$code_cwp, world_sf$code_cwp)
# 
# test <- t %>% dplyr::group_by(code, source) %>% slice(1)
# tm_shape(st_as_sf(t))+tm_polygons()+tm_fill(col = "source")
# 
IOTC <- world_sf[IOTC_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(iotc = "iotc")

IATTC <- world_sf[IATTC_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(iattc = "iattc")

WCPFC <- world_sf[WCPFC_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(wcpfc = "wcpfc")

ICCAT <- world_sf[ICCAT_shape,]%>% st_set_geometry(NULL) %>% dplyr::mutate(iccat = "iccat")



full_join <- dplyr::full_join(dplyr::full_join(dplyr::full_join(dplyr::full_join(world_sf, IOTC), IATTC), WCPFC), ICCAT) %>% st_set_geometry(NULL) 


full_join[is.na(full_join)] <-  FALSE

full_join <- full_join %>% dplyr::mutate(area_competence = as.factor(gsub("FALSE","",paste0(iotc, iattc, wcpfc, iccat))))
world_sf$continent <- st_within(world_sf, continent) %>% lengths > 0 
world_sf$continent <- str_replace(world_sf$continent, "TRUE","continent")

world_sf <- dplyr::left_join(world_sf, full_join)

world_sf_with_competence_area <- world_sf %>% dplyr::mutate(area_competence = as.factor(gsub("FALSE","",paste0(iotc, iattc, wcpfc, iccat, continent))))


inner_join <- data %>% dplyr::inner_join(world_sf_with_competence_area, by = c("geographic_identifier"="code"))



all_the_data <- inner_join  %>% ungroup() %>% dplyr::group_by(geographic_identifier, st_area, unit, source_authority, area_competence) %>% dplyr::summarise(value= sum(value, na.rm = TRUE))%>% dplyr::distinct() %>% dplyr::inner_join(world_sf%>% dplyr::select(-area_competence) , by = c("geographic_identifier"="code", "st_area") ) %>% dplyr::select(geographic_identifier, st_area, value, geom, unit, source_authority, area_competence)

mislocated_continent <- all_the_data %>% dplyr::filter(str_detect(area_competence, "continent"))



```

```{r}
mislocated_continent_init <- rawdata %>% semi_join(mislocated_continent, by = "geographic_identifier")
```

```{r}
# titre_1 <- "Mislocated tons"
# mislocated <-  pie_chart_1(fishingfleet,mislocated_continent_init %>% dplyr::filter(unit %in%c("MTNO","MT")))
# titre_1 <- "Original tons"
# 
# original <-  pie_chart_1(fishingfleet,rawdata%>% dplyr::filter(unit %in%c("MTNO","MT")))
# 
# plot_grid(mislocated, original)

studycatchesird::pie_chart_2(fishingfleet,mislocated_continent_init,rawdata)

```

Spain is mislocating the data a lot, as well as EUIRL and BLZ.

```{r}
# titre_1 <- "Mislocated numbers"
# mislocated <-  pie_chart_1(fishingfleet,mislocated_continent_init %>% dplyr::filter(unit %in%c("NOMT","NO")))
# titre_1 <- "Original numbers"
# 
# original <-  pie_chart_1(fishingfleet,mapped_data%>% dplyr::filter(unit %in%c("NOTM","NO")))
# 
# plot_grid(mislocated, original)
studycatchesird::pie_chart_2(fishingfleet,mislocated_continent_init,rawdata)

```

In numbers, it is Brasil, SYC and USA that are mislocating the data.

```{r}
# titre_1 <- "Mislocated tons"
# mislocated <-  pie_chart_1(species,mislocated_continent_init %>% dplyr::filter(unit %in%c("MTNO","MT")))
# titre_1 <- "Original tons"
# 
# original <-  pie_chart_1(species,mapped_data%>% dplyr::filter(unit %in%c("MTNO","MT")))
# 
# plot_grid(mislocated, original)
studycatchesird::pie_chart_2(species,mislocated_continent_init,rawdata)

```

Albacore is mislocated, as well as BET. 

```{r}

# mislocated_continent <- mislocated_continent %>% st_set_geometry(NULL)
# st_geometry(mislocated_continent) <- NULL

located_on_continent <- rawdata %>% semi_join(mislocated_continent , by = "geographic_identifier")
conversion_factor_above_500_kilos <- rawdata  %>% semi_join(absurd_conversion_factor%>% dplyr::mutate(time_start = as.character(time_start), time_end = as.character(time_end)))
a <- gdata::combine(located_on_continent, conversion_factor_above_500_kilos) %>% dplyr::rename(issue = source)
```

```{r}
# titre_1 <- "Problem conversion factor in tons"
# prblm_conv_fact <- pie_chart_1(source_authority,a%>% dplyr::filter(unit %in%c("MTNO","MT")))
# titre_1 <- "Original tons"
# 
# original <-  pie_chart_1(source_authority,mapped_data%>% dplyr::filter(unit %in%c("MTNO","MT")))
# plot_grid(prblm_conv_fact,original)
studycatchesird::pie_chart_2(source_authority,mislocated_continent_init,rawdata)

```

Problem of conversion factor seems to be coming from WCPFC and IATTC.

```{r message=FALSE, warning=FALSE}
source_authority <- c("IATTC", "IOTC","WCPFC","CCSBT","ICCAT")

lapply(source_authority, function(x){assign(paste0("table_",x), a #%>% dplyr::filter(source_authority ==x)
                                            , envir = .GlobalEnv)
  write.csv(paste0("table_",x), file = paste0("data/issues_with_data_table",x,".csv"))})



```

