---
title: "Etude SBF"
output:
  html_document: default
  word_document: default
date: '2022-03-23'
params:
  working_directory: "~/Documents/Tunaatlas_level1/jobs/20220428104014"
---

This document give a quick analysis of different way to handle the treatment of the Southern Bluefin Tuna in the Global Tuna Atlas. 

It explains how it was done before and how we propose it to be done now, showing the differences and remains open to modification/proposition.

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE
)
library(readtext)
library(flextable)
set_flextable_defaults(
  font.size = 30,
  font.color = "black",
  table.layout = "fixed",
  digits = NULL,
  theme_fun = "theme_box"
  )
options(scipen=999)
library(dplyr)
library(stringr)
library(readr)
library(webshot)
if(require("htmltools"))
div(flextable_html_dependency())
```

```{r}
mapping_codelist <- readRDS("data/mapping_codelist.rds")
initial_SBF <- mapping_codelist%>% filter(species == "SBF")
```

# Current version

For now, what is done is remove all the SBF catches (in tons and numbers) coming from a source authority different than CCSBT.

```{r}
#Paul treatment 
Actual  <- initial_SBF[ which(!(initial_SBF$species %in% "SBF" & initial_SBF$source_authority %in% c("ICCAT","IOTC","IATTC","WCPFC"))), ]%>% filter(species == "SBF")

```

# Issue with this method

For some years, or gears, the availibility of SBF catches is only coming from CTOI or ICCAT.

```{r}
# My treatment
source("https://raw.githubusercontent.com/BastienIRD/Tunaatlas_level1/main/fonction_overlap.R")

georef_dataset <- function_overlapped(dataset = initial_SBF, con =con, rfmo_to_keep = "CCSBT",
                                                 rfmo_not_to_keep = "IOTC", 
                                                 strata =c(   "species", "time_start", "time_end",  "unit"))
georef_dataset <- function_overlapped(dataset = georef_dataset, con =con, rfmo_to_keep = "CCSBT",
                                                 rfmo_not_to_keep = "CCSBT", 
                                                 strata =c(    "species", "time_start", "time_end",
                                                                                                                                "unit"))

Proposition <- georef_dataset %>% filter(species == "SBF")
```

```{r}
comp <- gdata::combine(initial_SBF, Actual, Proposition)
comp$unit <- str_replace(comp$unit, "MTNO","MT")
comp$unit <- str_replace(comp$unit, "NOMT","NO")
comp <-  comp%>% group_by(source, time_start, unit) %>% summarise(Value = sum(value)) %>% mutate(time_start = as.Date(time_start)) 
```


```{r}
library(lubridate)
comp_year <- comp %>% mutate(Year =lubridate::year(time_start)) %>%ungroup() %>%  group_by(Year, unit, source) %>% summarise(Value = sum(Value))
```
```{r}
library(ggplot2)

ggplot(comp_year)+
  aes(x = Year, y = Value, colour = source) +
  geom_line(size = 0.5) +
  scale_color_hue(direction = 1) +
  theme_minimal() +
  facet_wrap(vars(unit), scales = "free_y")
```



The difference between the two dataset is `r sum((Actual %>% filter(unit == "MT"))$value) - sum((Proposition %>% filter(unit == "MT"))$value)` in tons and `r sum((Actual %>% filter(unit == "NO"))$value) - sum((Proposition %>% filter(unit == "NO"))$value)` in number of fish.

# Other proposition 

We could also decide to keep the data from other rfmo's if there is no equivalent in year, area. 

The results would be the following : 

```{r}
# My treatment
source("https://raw.githubusercontent.com/BastienIRD/Tunaatlas_level1/main/fonction_overlap.R")

georef_dataset <- function_overlapped(dataset = mapping_codelist, con =con, rfmo_to_keep = "CCSBT",
                                                 rfmo_not_to_keep = "IOTC", 
                                                 strata =c("geographic_identifier",    "species", "time_start", "time_end",  "unit"))
georef_dataset <- function_overlapped(dataset = georef_dataset, con =con, rfmo_to_keep = "CCSBT",
                                                 rfmo_not_to_keep = "CCSBT", 
                                                 strata =c("geographic_identifier",    "species", "time_start", "time_end",
                                                                                                                                "unit"))

Proposition <- georef_dataset %>% filter(species == "SBF")


```


```{r}
comp <- gdata::combine(initial_SBF, Actual, Proposition)
comp$unit <- str_replace(comp$unit, "MTNO","MT")
comp$unit <- str_replace(comp$unit, "NOMT","NO")
comp <-  comp%>% group_by(source, time_start, unit) %>% summarise(Value = sum(value)) %>% mutate(time_start = as.Date(time_start)) 
```

```{r}

comp_year <- comp %>% mutate(Year =lubridate::year(time_start)) %>%ungroup() %>%  group_by(Year, unit, source) %>% summarise(Value = sum(Value))
ggplot(comp_year)+
  aes(x = Year, y = Value, colour = source) +
  geom_line(size = 0.5) +
  scale_color_hue(direction = 1) +
  theme_minimal() +
  facet_wrap(vars(unit), scales = "free_y")
```


The difference between the two dataset is `r sum((Actual %>% filter(unit == "MT"))$value) - sum((Proposition %>% filter(unit == "MT"))$value)` in tons and `r sum((Actual %>% filter(unit == "NO"))$value) - sum((Proposition %>% filter(unit == "NO"))$value)` in number of fish.

For more advanced comparison between the two dataset, please check: