---
title: "Number of strata with conversion factor"
output: html_document
date: '2022-03-23'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(readtext)
library(flextable)
set_flextable_defaults(
  font.size = 30,
  font.color = "black",
  table.layout = "fixed",
  digits = NULL,
  theme_fun = "theme_box"
  )
library(dplyr)
library(stringr)
library(readr)
```

```{r}
rdslevel0 <- readRDS("~/Documents/Tunaatlas_level1/jobs/20220322194525/entities/global_catch_ird_level2/OverlappingIATTCWCPFC/rds.rds") 

rds_level_0_strata <-rdslevel0 %>% select(-c(value, unit
             # , schooltype, catchtype, fishingfleet
                     ))%>% distinct()

strata_no <- rdslevel0 %>% filter(unit %in% c("no","NO")) %>% select(-c(value, unit
             # , schooltype, catchtype, fishingfleet
                     ))%>% distinct()
strata_t <- rdslevel0 %>% filter(unit %in% c("t","MT")) %>% select(-c(value, unit
             # , schooltype, catchtype, fishingfleet
                     ))%>% distinct()
```

There are `r nrow(strata_no)` strata at the end of level0 which are declared in number.
There are `r nrow(strata_t)` strata at the end of level0 which are declared in tons.


```{r}
rdslevel1 <- readRDS("~/Documents/Tunaatlas_level1/jobs/20220322194525/entities/global_catch_ird_level2/level1conversion/rds.rds")

rds_level_1_strata <- rdslevel1 %>% select(-c(value, unit
                   # ,  schooltype, catchtype, fishingfleet
         ))%>% distinct()

percent_strata_loss_level0_level1 <- round(100*(nrow(rds_level_0_strata)-nrow(rds_level_1_strata))/nrow(rdslevel0))
number_strata_loss_level0_level1 <- (nrow(rds_level_0_strata)-nrow(rds_level_1_strata))

conversion_factors_num_to_weight_ird_2021 <- read_csv("data/conversion_factors_num_to_weight_ird_2021.csv") 

  strata <- conversion_factors_num_to_weight_ird_2021 %>% select(-c(unit,conversion_factor, unit_target)) %>% distinct()

  
```

There are `r number_strata_loss_level0_level1` strata that are loss between level0 and level 1 (`r percent_strata_loss_level0_level1` % of the total). This means there is no conversion done for those strata.

```{r}
strata_level1_converted <- round((nrow(rds_level_1_strata) - nrow(strata_t))/nrow(strata))

```


However, the number of strata in the file of Alain Biseau, is `r nrow(strata)`. Which means each conversion factor is used for (in means) `r strata_level1_converted` strata.