---
title: 'Comparison of two data sets at different levels/options of the tuna atlas'
author: "IRD"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    toc: !expr if(!exists('child')) {TRUE} else {child}
    number_sections: TRUE
    keep_tex: true
  bookdown::html_document2:
    toc: !expr if(!exists('child')) {TRUE} else {child}
    number_sections: TRUE
params: 
  final: "~/Documents/Tunaatlas_level1/jobs/Level2FAL/entities/global_catch_1deg_level2/Markdown/Level2_RF1"
  dbname: "tunaatlas_sandbox2"
  host: "localhost"
  port: 5432
  user: "tunaatlas_u"
  password: "21c0551e7ed2911"
  further_analysis: "FALSE"
  filter_species: !r NULL
  filter_source_authority: !r NULL
  filter_gear: !r NULL
  filter_fishingfleet: !r NULL  
  filter_time_start: !r NULL
  filter_time_end: !r NULL
  filter_cat_geo: !r NULL
  filter_catchtype: !r NULL
  filter_schooltype: !r NULL
  filter_species_group: !r NULL
  titre_dataset_1: !r NULL
  titre_dataset_2: !r NULL
  fact: "catch"
  colnames_to_keep: [ fishingfleet ,           species ,                  
  unit ,                  value ,                 source_authority ]
  columns_to_keep: [  Precision     ,                   unit      ,                     
  "Captures table 1"      ,"Captures table 2"      ,                               "Loss / Gain",
   Difference (in %)          ,      Dimension   ,       Difference in millions of tons/fish ]
  con: con
  entity: entity
  config: config
  action: action
  short: FALSE
---

```{r}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE, fig.align = 'center'
)
```


```{r message=FALSE}

knitr::knit_hooks$set(inline = function(x) {   if(!is.numeric(x)){     x   }else{    prettyNum(round(x,2), big.mark=",")    } })

if(!(require(base))){ 
  install.packages("base") 
  (require(base))} 
if(!(require(flextable))){ 
  install.packages("flextable") 
  (require(flextable))} 
if(!(require(remotes))){ 
  install.packages("remotes") 
  (require(remotes))} 
if(!(require(utils))){ 
  install.packages("utils") 
  (require(utils))} 
if(!(require(stringr))){ 
  install.packages("stringr") 
  (require(stringr))} 
if(!(require(knitr))){ 
  install.packages("knitr") 
  (require(knitr))} 
if(!(require(DBI))){ 
  install.packages("DBI") 
  (require(DBI))} 
if(!(require(odbc))){ 
  install.packages("odbc") 
  (require(odbc))} 
if(!(require(sf))){ 
  install.packages("sf") 
  (require(sf))} 
if(!(require(dplyr))){ 
  install.packages("dplyr") 
  (require(dplyr))} 
if(!(require(kableExtra))){ 
  install.packages("kableExtra") 
  (require(kableExtra))} 
if(!(require(readxl))){ 
  install.packages("readxl") 
  (require(readxl))} 
if(!(require(readr))){ 
  install.packages("readr") 
  (require(readr))} 
if(!(require(tidyr))){ 
  install.packages("tidyr") 
  (require(tidyr))} 
if(!(require(ggplot2))){ 
  install.packages("ggplot2") 
  (require(ggplot2))} 
if(!(require(stats))){ 
  install.packages("stats") 
  (require(stats))} 
if(!(require(RColorBrewer))){ 
  install.packages("RColorBrewer") 
  (require(RColorBrewer))} 
if(!(require(cowplot))){ 
  install.packages("cowplot") 
  (require(cowplot))} 
if(!require(sutdycatchesird)){
  if(!require(remotes)){
    install.packages("remotes")
  }
  require(remotes)
  install_github("BastienIRD/sutdycatchesird")
  require(sutdycatchesird)
}
if(!(require(tmap))){ 
  install.packages("tmap") 
  (require(tmap))} 
if(!(require(RPostgreSQL))){ 
  install.packages("RPostgreSQL") 
  (require(RPostgreSQL))} 
if(!(require(officer))){ 
  install.packages("officer") 
  (require(officer))} 



#set the table caption styling
# knitr::opts_chunk$set(tab.cap.pre = "Table ", tab.cap.sep = ": ")

#set the table caption styling
if(!child){autonum <- officer::run_autonum(seq_id = "tab", bkm = "TC1", bkm_all = TRUE) # number the table, bkm (bookmark) is important as the cross-referencing is done using the bookmark
}



last_path = function(x){tail(stringr::str_split(x,"/")[[1]],n=1)}
plotting_type <- "plot" 
if (knitr::is_html_output()){plotting_type <- "view" }
```


```{r include=FALSE}
if(!exists("child")){child = FALSE} else{child = child}
```





```{r}
fonction_groupement = function(x, data){
  x  <-   enquo(x)
  groupement_1  <-   data %>% group_by(!!x,unit) %>% summarise(value_sum_1 = sum(value, na.rm=TRUE), number_lines1 = n()) %>%mutate(value_sum1 = ifelse(is.na(value_sum_1), 0, value_sum_1)) 
  second_highest_value <- groupement_1 %>% group_by(unit) %>%   arrange(desc(value_sum1)) %>% 
  slice(seq_len(2)) %>% arrange(value_sum1) %>% slice(seq_len(1)) %>% select(unit, second_highest_value = value_sum1)
  groupement2 <- groupement_1%>%inner_join(second_highest_value) %>%  group_by(unit) %>%  mutate(mean = mean(value_sum1))
}
```


```{r}

fonction_filtre = function(dataframe_tot_filter) {
  if(parameter_fact == "catch"){dataframe_tot_filter <- dataframe_tot_filter %>% dplyr::left_join(species_group%>% dplyr::distinct(), by = c("species"))
    dataframe_tot_filter <- dataframe_tot_filter %>% dplyr::left_join(cl_cwp_gear_level2, by = c("gear" = "Code"))
  if ("Name_En"%in% colnames(dataframe_tot_filter)){dataframe_tot_filter <- dataframe_tot_filter%>% dplyr::rename(Gear = Name_En)%>%dplyr::mutate(gear = as.character(gear))
  }}
  if (! is_null_exist(parameter_filter_species)){
    dataframe_tot_filter <-  dataframe_tot_filter %>%dplyr::filter(
      species %in% parameter_filter_species)
  }
  if (! is_null_exist(parameter_filter_gear)){
    dataframe_tot_filter <-  dataframe_tot_filter %>%dplyr::filter(
      gear %in% parameter_filter_gear)
  }    
  if (! is_null_exist(parameter_filter_source_authority )){
    dataframe_tot_filter <-  dataframe_tot_filter %>%dplyr::filter(
      source_authority %in% parameter_filter_source_authority)
  }  
  if (! is_null_exist(parameter_filter_fishingfleet )){
    dataframe_tot_filter <-  dataframe_tot_filter %>%dplyr::filter(
      fishingfleet %in% parameter_filter_fishingfleet)
  }
  if (! is_null_exist(parameter_filter_time_start )){
    dataframe_tot_filter <-  dataframe_tot_filter %>%dplyr::filter(
      time_start %in% parameter_filter_time_start)
  }
  if (! is_null_exist(parameter_filter_time_end )){
    dataframe_tot_filter <-  dataframe_tot_filter %>%dplyr::filter(
      time_end %in% parameter_filter_time_end)
  }
  if (! is_null_exist(parameter_filter_schooltype )){
    dataframe_tot_filter <-  dataframe_tot_filter %>%dplyr::filter(
      schooltype %in% parameter_filter_schooltype)
  }
  if (! is_null_exist(parameter_filter_catchtype )){
    dataframe_tot_filter <-  dataframe_tot_filter %>%dplyr::filter(
      catchtype %in% parameter_filter_catchtype)
  }
  
  if (! is_null_exist(parameter_filter_cat_geo )){
    dataframe_tot_filter <-  dataframe_tot_filter %>%dplyr::filter(
      cat_geo %in% parameter_filter_cat_geo)
  }
  if (! is_null_exist(parameter_filter_catchtype )){
    dataframe_tot_filter <-  dataframe_tot_filter %>%dplyr::filter(
      cat_geo %in% parameter_filter_catchtype)
  }
  
  if (! is_null_exist(parameter_filter_species_group )){
    dataframe_tot_filter <-  dataframe_tot_filter %>%dplyr::filter(
      species_group %in% parameter_filter_species_group)
    
  }
  dataframe_tot_filter <- dataframe_tot_filter%>%dplyr::mutate(unit = case_when(unit %in% c("MT","t","MTNO", "Tons")~ "Tons", unit %in% c("NO", "NOMT","no", "Number of fish")~"Number of fish")) 
  
}





init <- fonction_filtre(readRDS(paste0(as.character(parameter_final),"/rds.rds"))%>%dplyr::select(all_of(colnames_to_keep))) %>%   left_join(shape_without_geom, by = c("geographic_identifier"="code"))  %>%dplyr::mutate(time_start =as.character(time_start))%>%dplyr::mutate(time_end =as.character(time_end))%>%dplyr::mutate(cat_geo = as.character(cat_geo))


```


```{r}
carte_init <- fonction_groupement(geographic_identifier,mapped_data%>% mutate(unit = case_when(unit == "NOMT"~ "NO", unit == "MTNO"~"MT", TRUE ~ unit))) #%>% mutate(absurd = topn(value,2))

absurd = function(x){x %>% select(-value_sum_1) %>% filter(value_sum1 > 1.1 * second_highest_value & value_sum1 > 2*mean)}
absurd_cart <- absurd(carte_init)
```

Analyse for years/species :



```{r}
year_init <- mapped_data%>% mutate(unit = case_when(unit == "NOMT"~ "NO", unit == "MTNO"~"MT", TRUE ~ unit))%>% group_by(time_start, species,unit) %>% summarise(value_sum_1 = sum(value, na.rm=TRUE), number_lines1 = n()) %>%mutate(value_sum1 = ifelse(is.na(value_sum_1), 0, value_sum_1))

  second_highest_value <- year_init %>% group_by(unit) %>%   arrange(desc(value_sum1)) %>%
  slice(seq_len(2)) %>% arrange(value_sum1) %>% slice(seq_len(1)) %>% select(unit, second_highest_value = value_sum1)
  year_init_2 <- year_init%>%inner_join(second_highest_value) %>%  group_by(unit) %>%  mutate(mean = mean(value_sum1))

absurd_year <- year_init_2 %>% select(-value_sum_1) %>% filter(value_sum1 > 1.1 * second_highest_value & value_sum1 > 2*mean)
```

Maybe absurd it is just because it is declared this time in number and it used to be in tons.

Let's check the catches of FRI in 1990.

```{r}
FRI_catches <- mapped_data %>% filter(species == "FRI")

FRI_catches_by_year <- FRI_catches %>% group_by(time_start, unit) %>% summarise(value = sum(value))
```


# Years with catches superior than 2 times the mean and 10 percent of the second highest.

```{r}
qflextable(absurd_year)
```

For this year, we check in details the data.

```{r}
absurd_year_init <- semi_join(mapped_data, absurd_year, by = c("unit", "time_start"))

second_highest_value <- absurd_year_init %>% group_by(unit, time_start) %>%   arrange(desc(value)) %>%
  slice(seq_len(2)) %>% arrange(value) %>% slice(seq_len(1)) %>% select(unit, second_highest_value = value)
absurd_year_init <- absurd_year_init%>%inner_join(second_highest_value) %>%  group_by(unit) %>%  mutate(mean = mean(value))

absurd_year_init_absurd <- absurd_year_init %>% filter(value > 1.1 * second_highest_value & value > 2*mean)
```


```{r}
qflextable(absurd_year_init_absurd)
```

# Areas with catches superior than 2 times the mean and 10 percent of the second highest.

```{r}
qflextable(absurd_cart)
```


Those are the data for a geographical identifier of the same size and for a time period of the same length, in which the catches are superior of 10% the second highest value and superior to the double of the mean.
Let's check those catches.

```{r}
geograph_strange <- mapped_data %>% filter(geographic_identifier =="6440005" & unit %in%c("MTNO","NOMT"))

pie_chart_2 = function(x, init= init) {
  r <- deparse(substitute(x))
  colnames <- enquo(x)
  provisoire_i <-init %>%  group_by(!!colnames )%>% summarise(value = sum(value, na.rm = TRUE))  %>% arrange(desc(value)) %>%   mutate(id = row_number())%>%  
    mutate(class = as.factor(ifelse(id<4,!!colnames,"Others"))) %>%
    group_by(class) %>%  summarise(value = sum(value, na.rm = TRUE))%>%ungroup()%>% 
    select(  value, class)  %>% mutate(pourcentage = prop.table(value)*100)%>%
    mutate(labels = paste0(pourcentage," ",  " % "))%>% arrange(desc(class))%>%
  mutate(ypos_ligne = cumsum(pourcentage)- 0.5*pourcentage ) %>%
    distinct()
  
  
  
ggplot_i <- ggplot(provisoire_i) +
  aes(
    x = "",
    fill = class,
    colour = class,
    group = class,
    weight = pourcentage
  ) +
  geom_bar(position = "fill") +
  scale_fill_hue(direction = 1) +
  scale_color_hue(direction = 1) +
  theme_minimal()+ coord_polar("y", start=0)+ geom_text(data = (provisoire_i %>% mutate_if(is.numeric, round)), size = 3,
                           aes( x = 1 ,y = ypos_ligne/100, label = paste0(pourcentage,"%")), color = "black")+
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank())+
  labs(x = "", y="")
  


title <- ggdraw() + 
  draw_label(
    paste0("Distribution in value for the dimension : ",r),
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

graph <- plot_grid(ggplot_i,labels = c(paste0( titre_1)),
  label_size = 10)

plot_grid(
  title, graph,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1))+
    theme(plot.background = element_rect(color = "black"))


}

titre_1 <- "For 6440005"
plot_grid(pie_chart_2(fishingfleet, geograph_strange), pie_chart_2(source_authority, geograph_strange))

```

The issue could be that for this area, spain give catches in number and not in tons. This support the fact that data should be harmonized in units to make futher analysis.

## Data present in georef dataset but not in nominal

```{r}
getwd()
nominal <- readRDS("~/Documents/Tunaatlas_level1/jobs/20220511123321/entities/global_nominal_catch_firms_level0/Markdown/rawdata/rds.rds")%>% mutate(year = lubridate::year(time_start))#%>% filter(species_group == "Tropical tunas")
data<- readRDS("~/Documents/Tunaatlas_level1/jobs/20220511123321/entities/global_catch_firms_Bastien_rds_level2/Markdown/rawdata/rds.rds") %>% mutate(year = lubridate::year(time_start))


rfmo_year_species_common <- inner_join(nominal %>% dplyr::select(species, year, source_authority) %>% distinct(), data %>% dplyr::select(species, year, source_authority)%>% distinct())

rfmo_year_species_not_common <- gdata::combine(nominal =anti_join(nominal %>% dplyr::select(species, year, source_authority) %>% distinct(), data %>% dplyr::select(species, year, source_authority)%>% distinct()),data=anti_join(data %>% dplyr::select(species, year, source_authority) %>% distinct(), nominal %>% dplyr::select(species, year, source_authority)%>% distinct()))
```

```{r}
if(!require(sutdycatchesird)){
  if(!require(devtools)){
    install.packages("devtools")
  }
  require(devtools)
  install_github("BastienIRD/sutdycatchesird")
  require(sutdycatchesird)
}
georef_without_nominal_equivalent <- data %>% inner_join(rfmo_year_species_not_common %>% filter(source=="data"))
summary(summary_fish(georef_without_nominal_equivalent))

summary_fish(georef_without_nominal_equivalent)
```

More than 2 millions tons are present in georef dataset and not in nominal (at this we could add all the catches in number of fish)

### Features of the data present only in georef

```{r}
titre_1 <- "Data in georef without equivalent in nominal"
pie_chart_2(species,georef_without_nominal_equivalent %>% filter(unit=="MT"))

pie_chart_2(fishingfleet,georef_without_nominal_equivalent%>% filter(unit=="MT"))

pie_chart_2(source_authority,georef_without_nominal_equivalent%>% filter(unit=="MT"))

```

```{r}
rfmo_in_coomun <- inner_join(nominal %>% select(-c(value, time_start, time_end, geographic_identifier)) %>% distinct(), data %>%select(-c(geographic_identifier,value, time_start, time_end))%>% distinct())

data <- data%>% filter(unit%in%c("MT","MTNO"))

rfmo_not_in_coomun <- gdata::combine(nominal =anti_join(nominal %>% dplyr::select(-c(value, time_start, time_end, geographic_identifier,unit)) %>% distinct(), data %>% dplyr::select(-c(value, time_start, time_end, geographic_identifier,unit))%>% distinct()) ,data=anti_join(data %>% dplyr::select(-c(value, time_start, time_end, geographic_identifier,unit)) %>% distinct(), nominal %>% dplyr::select(-c(value, time_start, time_end, geographic_identifier,unit))%>% distinct())%>% select(-c(catchtype, schooltype)))
```

```{r}

nrow(rfmo_not_in_coomun %>% filter(source=="nominal"))
nrow(rfmo_not_in_coomun %>% filter(source=="data"))

nominal_only <- rfmo_not_in_coomun %>% filter(source=="nominal") %>% inner_join(nominal) %>% filter(unit=="MT")
georef_only <- rfmo_not_in_coomun %>% filter(source=="data") %>% inner_join(data)
titre_1 <- "Nominal only"
pie_chart_2(species, nominal_only)
titre_1 <- "Georef only"
pie_chart_2(species, georef_only)

titre_1 <- "Nominal only"
pie_chart_2(fishingfleet, nominal_only)
titre_1 <- "Georef only"
pie_chart_2(fishingfleet, georef_only)
```

