---
title: "Number of strata with conversion factor"
output:
  bookdown::pdf_document2:
    toc: !expr if(!exists('child')) {TRUE} else {child}
    number_sections: TRUE
    keep_tex: true
    extra_dependencies: ["adjustbox", "subfig"]
  bookdown::html_document2:
    toc: !expr if(!exists('child')) {TRUE} else {child}
    number_sections: TRUE
date: '2022-03-23'
params:
  final: "~/Documents/Tunaatlas_level1/jobs/20220927110301_global_catch/entities/global_catch_1deg_level1_final/Markdown/Modifying_IOTC_cwp_errors"
  rawdata: "data/rawdata"
  dbname: "tunaatlas"
  host: "db-tunaatlas.d4science.org"
  port: 5432
  user: "tunaatlas_u"
  password: "21c0551e7ed2911"
  plotting: "plot"
  world_coastline: "gshhs_world_coastlines"
  con: con
  filter_species: !r NULL

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

knitr::knit_hooks$set(inline = function(x) {   if(!is.numeric(x)){     x   }else{    prettyNum(round(x,2), big.mark=",")    } })

if(!(require(base))){ 
  install.packages("base") 
  (require(base))} 
if(!(require(flextable))){ 
  install.packages("flextable") 
  (require(flextable))} 
if(!(require(remotes))){ 
  install.packages("remotes") 
  (require(remotes))} 
if(!(require(utils))){ 
  install.packages("utils") 
  (require(utils))} 
if(!(require(stringr))){ 
  install.packages("stringr") 
  (require(stringr))} 
if(!(require(knitr))){ 
  install.packages("knitr") 
  (require(knitr))} 
if(!(require(DBI))){ 
  install.packages("DBI") 
  (require(DBI))} 
if(!(require(odbc))){ 
  install.packages("odbc") 
  (require(odbc))} 
if(!(require(rlang))){ 
  install.packages("rlang") 
  (require(rlang))} 
if(!(require(sf))){ 
  install.packages("sf") 
  (require(sf))} 
if(!(require(kableExtra))){ 
  install.packages("kableExtra") 
  (require(kableExtra))} 
if(!(require(readxl))){ 
  install.packages("readxl") 
  (require(readxl))} 
if(!(require(readr))){ 
  install.packages("readr") 
  (require(readr))} 
if(!(require(tidyr))){ 
  install.packages("tidyr") 
  (require(tidyr))} 
if(!(require(ggplot2))){ 
  install.packages("ggplot2") 
  (require(ggplot2))} 
if(!(require(stats))){ 
  install.packages("stats") 
  (require(stats))} 
if(!(require(RColorBrewer))){ 
  install.packages("RColorBrewer") 
  (require(RColorBrewer))} 
if(!(require(cowplot))){ 
  install.packages("cowplot") 
  (require(cowplot))} 
if(!require(sutdycatchesird)){
  if(!require(remotes)){
    install.packages("remotes")
  }
  require(remotes)
  install_github("BastienIRD/sutdycatchesird")
  require(sutdycatchesird)
}
if(!(require(tmap))){ 
  install.packages("tmap") 
  (require(tmap))} 
if(!(require(RPostgreSQL))){ 
  install.packages("RPostgreSQL") 
  (require(RPostgreSQL))} 
if(!(require(officer))){ 
  install.packages("officer") 
  (require(officer))} 
if(!(require(lubridate))){ 
  install.packages("lubridate") 
  (require(lubridate))} 
if(!(require(dplyr))){ 
  install.packages("dplyr") 
  (require(dplyr))} 

set_flextable_defaults(
  font.size = 10,
  font.color = "black",
  digits = 2,
  theme_fun = "theme_box"
)
```

```{r}
rdslevel0 <- readRDS("~/Documents/Tunaatlas_level1/jobs/20220927110301_global_catch/entities/global_catch_1deg_level1_final/Markdown/rawdata/rds.rds")

rds_level_0_strata <-rdslevel0 %>% select(-c(value, unit
             # , schooltype, catchtype, fishingfleet
                     ))%>% distinct()

strata_no <- rdslevel0 %>% filter(unit %in% c("no","NO")) %>% select(-c(value, unit
             # , schooltype, catchtype, fishingfleet
                     ))%>% distinct()
strata_t <- rdslevel0 %>% filter(unit %in% c("t","MT")) %>% select(-c(value, unit
             # , schooltype, catchtype, fishingfleet
                     ))%>% distinct()
```

There are `r nrow(strata_no)` strata at the end of level0 which are declared in number.
There are `r nrow(strata_t)` strata at the end of level0 which are declared in tons.


```{r}
rdslevel1 <- readRDS("~/Documents/Tunaatlas_level1/jobs/20220927110301_global_catch/entities/global_catch_1deg_level1_final/Markdown/raising/rds.rds")
rds_level_1_strata <- rdslevel1 %>% select(-c(value, unit
                   # ,  schooltype, catchtype, fishingfleet
         ))%>% distinct()

percent_strata_loss_level0_level1 <- round(100*(nrow(rds_level_0_strata)-nrow(rds_level_1_strata))/nrow(rdslevel0))
number_strata_loss_level0_level1 <- (nrow(rds_level_0_strata)-nrow(rds_level_1_strata))

conversion_factors_num_to_weight_ird_2021 <- read_csv("data/conversion_factors_num_to_weight_ird_2021.csv") 

  strata <- conversion_factors_num_to_weight_ird_2021 %>% select(-c(unit,conversion_factor, unit_target)) %>% distinct()

  
```

There are `r number_strata_loss_level0_level1` strata that are loss while raising on level 1 (`r percent_strata_loss_level0_level1` % of the total). This means there is no conversion done for those strata.

```{r}
strata_level1_converted <- round((nrow(rds_level_1_strata) - nrow(strata_t))/nrow(strata))
```


However, the number of strata in the file of Alain Biseau, is `r nrow(strata)`. Which means each conversion factor is used for (in means) `r strata_level1_converted` strata.

```{r}
mapping_codelist <-readRDS("~/Documents/Tunaatlas_level1/jobs/20220927110301_global_catch/entities/global_catch_1deg_level1_final/Markdown/mapping_codelist/rds.rds")
MTNO <- mapping_codelist %>% filter(unit == "MTNO")
NOMT <- mapping_codelist %>% filter(unit == "NOMT")
unique(MTNO$source_authority)
unique(NOMT$source_authority)
setdiff <- setdiff(NOMT %>% select(-c(value, unit)), MTNO %>% select(-c(value, unit)))
setdiff2 <- setdiff(MTNO %>% select(-c(value, unit)), NOMT %>% select(-c(value, unit)))
unique(setdiff$source_authority)
unique(setdiff2$source_authority)

conversion_factors_num_to_weight_ird_2021 <- read_csv("data/conversion_factors_num_to_weight_ird_2021.csv")%>% mutate_if(is.Date, as.character) %>% mutate(geographic_identifier = as.character(geographic_identifier))
```

There are `r nrow(conversion_factors_num_to_weight_ird_2021)` stratas converted in level 1.

```{r}
converted_level0 <- rbind(full_join(NOMT , MTNO, by = setdiff(colnames(MTNO), c("value", "unit") )) %>% rename(NO =value.x, MT = value.y) %>% select(-c(unit.y, unit.x)), full_join(MTNO , NOMT, by = setdiff(colnames(MTNO), c("value", "unit") )) %>% rename(MT =value.x, NO = value.y) %>% select(-c(unit.y, unit.x)))%>% distinct() %>% mutate(conversion_factor = MT/NO) #%>% full_join(test, by = c("geographic_identifier"="code")) %>% mutate(geographic_identifier = source) 

converted <- converted_level0 %>% select(setdiff(colnames(conversion_factors_num_to_weight_ird_2021),c("unit", "unit_target")))%>% distinct()
```

There are `r nrow(converted)` stratas converted in level 0.




```{r}
comparison_converted_factor <- inner_join(conversion_factors_num_to_weight_ird_2021%>% mutate_if(is.Date, as.character),converted_level0, by = c("gear", "time_start", "time_end", "geographic_identifier", "species"))

comparison_converted_factor_test <- inner_join(conversion_factors_num_to_weight_ird_2021%>% mutate_if(is.Date, as.character),converted_level0, by = c("gear", "time_start", "time_end", "species"))


```

# Comparison (for the data available) of the conversion factor of RFMOs and the conversion factor of Alain Biseau

```{r}
all_strata_only_one_unit_conversion <- rbind(setdiff, setdiff2) %>% inner_join(rbind(NOMT, MTNO))
```

First it is important to notice that on the data given by RFMO, several stratas are present only in NOMT or in NTMO.
Problem : Data in NOMT was removed in level 1 because it was hypothetically the same than in NTMO.
Those stratas are only provided by ICCAT.

```{r}

before_raising_no <- rdslevel0 %>% filter(unit %in% c("no","NO"))

all_strata_converted <- anti_join(before_raising_no %>% select(-c(value, unit)),all_strata_only_one_unit_conversion %>% select(-c(value, unit))) %>% distinct()
```

```{r}
con <- params$con


query <- "SELECT code, st_area(geom), geom from area.cwp_grid"
out <- try((world_sf <- st_read(con, query = query)), silent = TRUE)
if(!any(class(out) == "error")){con <- DBI::dbConnect(RPostgres::Postgres() , dbname = params$dbname, host = params$host,   port = params$port,
                  user = params$user,
                 password = params$password)}

query <- paste0("SELECT \n               u1.codesource_area as geographic_identifier,\n               u2.codesource_area as conv_factor_df_geo_id\n             FROM\n               area.area_labels u1,\n               area.area_labels u2\n             WHERE \n               u2.tablesource_area='", 
               "areas_conversion_factors_numtoweigth_ird", 
               "' \n               AND u2.codesource_area IN ('", 
               unique(conversion_factors_num_to_weight_ird_2021$geographic_identifier), 
               "') \n               AND u1.tablesource_area='", 
               "areas_tuna_rfmos_task2", "' \n               AND u1.codesource_area IN ('", 
               unique(before_raising_no$geographic_identifier), "') \n               AND ST_Contains(u2.geom, u1.geom)", 
               sep = "")
library(dbplyr)
query <- "SELECT  code,st_area(geom), geom from area.areas_conversion_factors_numtoweigth_ird"
area_conversion <- st_make_valid(st_read(con, query = query)) %>% filter(!is.na(st_area))

query <- "SELECT  code,st_area(geom), geom from area.areas_tuna_rfmos_task2"
area_converted <- st_make_valid(st_read(con, query = query)%>% filter(!st_is_empty(.)))
area_converted <-area_converted[(sf::st_is_valid(area_converted)),]
tmap_mode("view")
# tm_shape(area_conversion)+tm_polygons()
# tm_shape(area_converted)+tm_polygons()

area1 <- area_converted[st_within(st_as_sf(area_converted),st_as_sf(area_conversion %>% filter(code == 1))) %>% lengths >0,]
area2 <- area_converted[st_within(st_as_sf(area_converted),st_as_sf(area_conversion %>% filter(code == 2))) %>% lengths >0,]
area3 <- area_converted[st_within(st_as_sf(area_converted),st_as_sf(area_conversion %>% filter(code == 3))) %>% lengths >0,]
area0 <- area_converted[st_within(st_as_sf(area_converted),st_as_sf(area_conversion %>% filter(code == 0))) %>% lengths >0,]

test <- gdata::combine(area1, area2, area3, area0) %>% mutate(source = case_when(source == "area1" ~ 1, source == "area2"~2, source == "area3"~3, TRUE ~ 0))


all_strata_converted2 <- left_join(all_strata_converted, test %>% rename(geographic_identifier = code), by ="geographic_identifier")
```


```{r}
all_strata_converted2 <- all_strata_converted2 %>% mutate(source = as.character(source))
left_join <- left_join(all_strata_converted2  %>%  mutate(geographic_identifier = (source)), conversion_factors_num_to_weight_ird_2021 %>% mutate_if(is.Date, as.character) )

inner_join <- inner_join(all_strata_converted2%>% mutate(geographic_identifier = (source)), conversion_factors_num_to_weight_ird_2021 %>% mutate_if(is.Date, as.character) )
```

